---
title: "Chap1 kin nw"
output: html_document
```{r}
setwd("/Users/pranavsuresh/Code/WeaverYIRU20210811")
```
---

```{r}
#Import this and save all the process
# degree_KDNB <- read_xlsx("../output/kin network/output_degree network_KDNB_cm.xlsx") %>% setDT()
degree_KDNB <- read_xlsx("../output/kin network/output_degree network_KDNB_all.xlsx") %>% setDT()
```

```{r}
#[kinet.p]
#[degree_kin]
```



#------Kin nw by PLOT--------#
##first order
```{r}
#[kinet.p]----
#only first order
f <- function(x){
  node <- data.frame(node = x$color) %>% mutate(sex = fun_sex(x$color, sex)) %>% arrange(node)
  
  edgelist <- as.data.frame.matrix(t(combn(node$node, 2))) %>% 
    mutate(kinorder = fun_kinship(., kinship, "kinorder"), 
           kinorder2 = fun_kinship(., kinship, "kinorder2")) %>% 
    rename(id1=V1, id2=V2) %>% 
    filter(kinorder=="first")
  
  net <- graph.data.frame(d = edgelist, vertices = node, directed = F)
  return(net)
  }

#All birds
kinet.p <- data %>% 
  filter(color!="MYPO") %>% 
  select(year, plot, color) %>% 
  distinct() %>% 
  left_join(select(age, year, color, age), by=c("color", "year")) %>% 
  filter(age!="IM") %>% 
  split(list(.$year, .$plot), drop = T) %>% 
  map(., f)

#change list names 
for(i in 1:length(kinet.p)) {
    outputname <- paste0("net_", substr(names(kinet.p)[i], 3, 4), substr(names(kinet.p)[i], 6, 6)) #eg. adjm_15L
    names(kinet.p)[i] <- outputname  # name each object
}

#output kin net
#saveRDS(kinet.p, "../output/kin network/data/net_kinship_all.list.RData")
```

### plot kin network by plot
```{r}
#with labels
for(i in 1:length(kinet.p)){
   name = paste0("kinship,", names(kinet.p[i]))
  ggsave(paste0("../output/kin network/fig/colony_member/labels/plot/", name, ".png"), fun_plotkin(kinet.p[[i]],    netname = name, "kinorder2"), width = 6, height = 6)
}

#without labels
for(i in 1:length(kinet.p)){
   name = paste0("kinship,", names(kinet.p[i]))
  ggsave(paste0("../output/kin network/fig/colony_member/no label/plot/", name, ".png"), fun_plotkin(kinet.p[[i]], netname = name, "kinorder2", vname = "n"), width = 6, height = 6)
}

```

##first and second order
```{r}
#[kinet2.p]----
#only first order
f12 <- function(x){
  node <- data.frame(node = x$color) %>% mutate(sex = fun_sex(x$color, sex)) %>% arrange(node)
  
  edgelist <- as.data.frame.matrix(t(combn(node$node, 2))) %>% 
    mutate(kinorder = fun_kinship(., kinship, "kinorder"), 
           kinorder2 = fun_kinship(., kinship, "kinorder2")) %>% 
    rename(id1=V1, id2=V2) %>% 
    filter(kinorder=="first" | kinorder == "second")
  
  net <- graph.data.frame(d = edgelist, vertices = node, directed = F)
  return(net)
  }

#All birds
kinet2.p <- data %>% 
  filter(color!="MYPO") %>% 
  select(year, plot, color) %>% 
  distinct() %>% 
  left_join(select(age, year, color, age), by=c("color", "year")) %>% 
  filter(age!="IM") %>% 
  split(list(.$year, .$plot), drop = T) %>% 
  map(., f12)

#change list names 
for(i in 1:length(kinet2.p)) {
    outputname <- paste0("net_", substr(names(kinet2.p)[i], 3, 4), substr(names(kinet2.p)[i], 6, 6)) #eg. adjm_15L
    names(kinet2.p)[i] <- outputname  # name each object
}

#output kin net
#saveRDS(kinet2.p, "../output/kin network/data/net_kinship12_all.list.RData")
```

#Q:What is the size of kin network?
```{r}
f3 <- function(net){
  data <- data.frame(dg_first = degree(net)) %>% rownames_to_column(., "color")
  return(data)
}

#[degree_kin12]----
degree_kin12 <- kinet2.p %>% map(., f3) %>% rbindlist(., idcol = "net") %>% 
  rename(dg_firstsecond = dg_first) %>% 
  setDT()

#[degree_kin]----
degree_kin <- kinet.p %>% map(., f3) %>% rbindlist(., idcol = "net") %>% 
  left_join(degree_kin12, by=c("net", "color")) %>% 
  mutate(dg_second = dg_firstsecond - dg_first) %>% 
  mutate(sex = fun_sex(.$color, sex), 
         year = paste0("20", substr(net, 5, 6)), 
         plot = substr(net, 7, 7)) %>% 
  mutate(plot = recode(plot, "M"="MSTO", "S"="SPRA", "L"="LLOD")) %>% 
  left_join(select(age, color, year, age), by=c("color", "year")) %>% 
  setDT()

```

#Summary of kin nw by sex
```{r}
#sample size
degree_kin %>% select(color, sex) %>% distinct() %>% group_by(sex) %>% summarise(n=n())

#summary
sum_dg_kin_bysex <- degree_kin %>% 
  group_by(sex) %>% 
  summarise(mean_dg1 = mean(dg_first), sd_dg1 = sd(dg_first), 
            mean_dg2 = mean(dg_second), sd_dg2 = sd(dg_second), 
            mean_dg12 = mean(dg_firstsecond), sd_dg12 = sd(dg_firstsecond))

sum_dg_kin_bysexsite <- degree_kin %>% 
  group_by(plot, sex) %>% 
  summarise(mean_dg1 = mean(dg_first), sd_dg1 = sd(dg_first),
            mean_dg2 = mean(dg_second), sd_dg2 = sd(dg_second), 
            mean_dg12 = mean(dg_firstsecond), sd_dg12 = sd(dg_firstsecond))

sum_dg_kin_bysexsiteyear <- degree_kin %>% 
  group_by(year, plot, sex) %>% 
  summarise(mean_dg1 = mean(dg_first), sd_dg1 = sd(dg_first), 
            mean_dg2 = mean(dg_second), sd_dg2 = sd(dg_second), 
            mean_dg12 = mean(dg_firstsecond), sd_dg12 = sd(dg_firstsecond))
```

```{r}
write_xlsx(sum_dg_kin_bysex, "../output/kin network/output_sum_dg_kin_bysex_all.xlsx")
write_xlsx(sum_dg_kin_bysexsite, "../output/kin network/output_sum_dg_kin_bysexsite_all.xlsx")
write_xlsx(sum_dg_kin_bysexsiteyear, "../output/kin network/output_sum_dg_kin_bysexsiteyear_all.xlsx")
```



#Degree of sleeping nw
```{r}
f4 <- function(net){
  data <- data.frame(dg_N = degree(net), 
                     betw_N = betweenness(net),
                     dgw_N = graph.strength(net),
                     subc_N = subgraph_centrality(net)) %>% rownames_to_column(., "color")
  
  return(data)
}

#[degree_N]----
degree_N <- Nnet.pssa %>% map(., f4) %>% rbindlist(., idcol = "net") %>% 
  mutate(sex = fun_sex(.$color, sex), 
         year = paste0("20", substr(net, 5, 6)), 
         plot = substr(net, 7, 7)) %>% 
  mutate(plot = recode(plot, "M"="MSTO", "S"="SPRA", "L"="LLOD")) %>% 
  filter(color!="MYPO") %>% 
  setDT()

```

```{r}
f4.2 <- function(net){
  edgelist <- as.data.frame.matrix(get.edgelist(net)) %>% 
    mutate(kinorder = fun_kinship(., kinship, "kinorder"), 
           kinorder2 = fun_kinship(., kinship, "kinorder2")) %>% 
    rename(id1=V1, id2=V2) %>% 
    filter(kinorder=="first") %>% 
    select(id1, id2) %>% 
    as.matrix()
  
  net2 <- graph.edgelist(edgelist)

  data <- data.frame(dg_N_first = degree(net2)) %>% rownames_to_column(., "color")
  
  return(data)
}

#[degree_N_firt]----
degree_N_first <- Nnet.pssa %>% map(., f4.2) %>% rbindlist(., idcol = "net") %>% 
  mutate(sex = fun_sex(.$color, sex), 
         year = paste0("20", substr(net, 5, 6)), 
         plot = substr(net, 7, 7)) %>% 
  mutate(plot = recode(plot, "M"="MSTO", "S"="SPRA", "L"="LLOD")) %>% 
  filter(color!="MYPO") %>% 
  setDT()
```

#degree of Daytime networks
```{r}
f4.3 <- function(net){
  data <- data.frame(dg_D = degree(net), 
                     betw_D = betweenness(net), 
                     dgw_D = strength(net)) %>% rownames_to_column(., "color")
  return(data)
}

degree_D <- Dnet.pssa %>% map(., f4.3) %>% rbindlist(., idcol = "net") %>% 
  mutate(sex = fun_sex(.$color, sex), 
         year = paste0("20", substr(net, 5, 6)), 
         plot = substr(net, 7, 7)) %>% 
  mutate(plot = recode(plot, "M"="MSTO", "S"="SPRA", "L"="LLOD")) %>% 
  filter(color!="MYPO") %>% 
  setDT()

```

#degree of breeding network
```{r}
f5 <- function(net){
  data <- data.frame(dg_B = degree(net),
                     betw_B = betweenness(net)) %>% rownames_to_column(., "color")
  return(data)
}

#[degree_B]----
degree_B <- Bnet.p %>% map(., f5) %>% rbindlist(., idcol = "net") %>% 
  mutate(sex = fun_sex(.$color, sex), 
         year = paste0("20", substr(net, 5, 6)), 
         plot = substr(net, 7, 7)) %>% 
  mutate(plot = recode(plot, "M"="MSTO", "S"="SPRA", "L"="LLOD")) %>% 
  filter(color!="MYPO") %>% 
  setDT()

#[degree_KDNB]----
degree_KDNB <- degree_kin %>% 
  left_join(select(degree_D, year, plot, color, dg_D, betw_D, dgw_D), 
            by=c("year", "plot", "color")) %>% 
  left_join(select(degree_B, year, plot, color, dg_B, betw_B), 
            by=c("year", "plot", "color")) %>% 
  left_join(select(degree_N, year, plot, color, dg_N, betw_N, dgw_N, subc_N), 
            by=c("year", "plot", "color")) %>%
  left_join(select(degree_N_first, year, plot, color, dg_N_first), 
            by=c("year", "plot", "color")) %>%
  replace(is.na(.), 0) %>% setDT()


  
```

```{r}
write_xlsx(degree_KDNB, "../output/kin network/output_degree network_KDNB_all.xlsx")
```

#plot
```{r}
#---------------breeding vs. kin nw
ggscatter(degree_KDNB, x = "dg_first", y = "dg_B", facet.by = c("sex", "year"),
          size = 1, 
          add = "reg.line", conf.int = T, 
          xlab = "Degree in kin networks", 
          ylab = "Degree in breeding networks") +
    stat_cor(method = "pearson", label.x.npc = 0.2, size=2.5)+
    ggtitle("breeding vs. kin network") +
  geom_count()

ggsave("../output/kin network/fig/fig_B and kin nw_sexyear_cm.png", width = 7, height=4)

# #------------------breeding vs. sleeping nw
# ggscatter(degree_KDNB, x = "dg_N", y = "dg_B", facet.by = c("sex", "year"),
#           size = 1, xticks.by=2,
#           add = "reg.line", conf.int = T, 
#           xlab = "Degree in sleeping networks", 
#           ylab = "Degree in breeding networks") +
#     stat_cor(method = "pearson", label.x.npc = 0.1, size=2.5)+
#     ggtitle("breeding vs. sleeping network") +
#   geom_count()
# 
# ggsave("../output/kin network/fig/fig_B and N nw_sexyear_cm.png", width = 7, height=4)

#---------kin vs. sleeping
ggscatter(degree_KDNB, x = "dg_first", y = "dg_N", facet.by = c("sex","year"),
          size = 1, xticks.by = 2,
          add = "reg.line", conf.int = T, 
          xlab = "Degree in kin networks", 
          ylab = "Degree in sleeping networks") +
    stat_cor(method = "pearson", label.x.npc = 0.1, size=2.5)+
    ggtitle("sleeping network vs. kin network") +
  geom_count()

ggsave("../output/kin network/fig/fig_N and kin nw_sexyear_cm.png", width = 7, height=4)

#---------kin vs. sleeping first
ggscatter(degree_KDNB, x = "dg_first", y = "dg_N_first", facet.by = c("sex","year"),
          size = 1, xticks.by = 2,
          add = "reg.line", conf.int = T, 
          xlab = "Degree in kin networks", 
          ylab = "Degree in sleeping networks") +
    stat_cor(method = "pearson", label.x.npc = 0.1, size=2.5)+
    ggtitle("sleeping network vs. kin network") +
  geom_count()

ggsave("../output/kin network/fig/fig_N_first and kin nw_sexyear_cm.png", width = 7, height=4)


#--------------breeding and sleeping with first
ggscatter(degree_KDNB, x = "dg_N_first", y = "dg_B", facet.by = c("sex","year"),
          size = 1, xticks.by = 2,
          add = "reg.line", conf.int = T, 
          xlab = "Degree in sleeping networks (first)", 
          ylab = "Degree in breeding networks") +
    stat_cor(method = "pearson", label.x.npc = 0.1, size=2.5)+
    ggtitle("sleeping network vs. breeding network") +
  geom_count()

ggsave("../output/kin network/fig/fig_N_first and B_sexyear_cm.png", width = 7, height=4)
```

#pre-modeling tidy
```{r}
degree_KDNB$sex <- factor(degree_KDNB$sex)
degree_KDNB$year <- factor(degree_KDNB$year)
```

#Do males have larger kin nw
#GLMER 
```{r}
library(glmmTMB)
source("overdisp_fun.R")

#full model, first and second order----
fit <- glmmTMB(dg_firstsecond ~ sex*plot + (1|year) + (1|color), family = poisson,  data=degree_kin)

#diagnostic: ok
overdisp_fun(fit)  #no overdispersion
resd <- DHARMa::simulateResiduals(fit)  #simulation output
plot(resd)

summary(fit)
glmmTMB:::Anova.glmmTMB(fit)

emm.fit <- emmeans(fit, pairwise ~ sex*plot, type = "response")
plot(emm.fit)

#----first order----
fit1 <- glmmTMB(dg_first ~ sex*plot + (1|year) + (1|color), family = poisson, ziformula = ~ 1,  data=degree_kin)

#diagnostic: ok
resd <- DHARMa::simulateResiduals(fit1)  #simulation output
plot(resd)

summary(fit1)
glmmTMB:::Anova.glmmTMB(fit1)

emm.fit1 <- emmeans(fit1, pairwise ~ sex*plot, type = "response")
plot(emm.fit1)
```
#------------END of Kin network by PLOT-----------#

#-------------kin network by COLONY------------#
```{r}
#[kinet.c]----
kinet.c <- colony_member %>% 
  filter(colony!="SPRA51" & colony!="SPRA24" & color!="MYPO") %>% #only 1bird
  select(year, plot, colony, color) %>% 
  distinct() %>% 
  split(list(.$year, .$colony), drop = T) %>% 
  map(., f)

#saveRDS(kinet.c, "../output/kin network/data/net_kinship_colony_cm.list.RData")
```

#Summary of kin nw by colony
```{r}
#[degree_kin_c]----
degree_kin_c <- kinet.c %>% map(., f3) %>% rbindlist(., idcol = "net") %>% 
  mutate(sex = fun_sex(.$color, sex), 
         year = substr(net, 1, 4), 
         plot = substr(net, 6, 9), 
         colony = substr(net, 6, 11)) %>%
  add_count(net) %>% 
  filter(color!="MYPO") %>% 
  setDT()

#degree first by colony
sum_degree_kin_c <- degree_kin_c %>% 
  group_by(year, plot, colony) %>% 
  summarise(mean_dg1 = mean(dg_first), sd_dg1 = sd(dg_first))

#average over all colonies
sum_degree_kin_c_all <- degree_kin_c %>% 
  summarise(mean_dg1 = mean(dg_first), sd_dg1 = sd(dg_first))
```


### plot kin network at colony levels
```{r}
#with labels
for(i in 1:length(kinet.c)){
   name = paste0("kinship,", names(kinet.c[i]))
  ggsave(paste0("../output/kin network/fig/colony_member/labels/colony/", name, ".png"), fun_plotkin(kinet.c[[i]],    netname = name, "kinorder2"), width = 6, height = 6)
}

#without labels
for(i in 1:length(kinet.c)){
   name = paste0("kinship,", names(kinet.c[i]))
  ggsave(paste0("../output/kin network/fig/colony_member/no label/colony/", name, ".png"), fun_plotkin(kinet.c[[i]], netname = name, "kinorder2", vname = "n"), width = 6, height = 6)
}
```

#-----------Network analysis--------------#
```{r}
Dnet.p
```

```{r}
library(readxl)
library(writexl)
library(data.table)
library(dplyr)
library(purrr)
library(tibble)
library(igraph)
library(stringr)
library(ggplot2)
library(ggpubr)
library(forcats)
library(glmmTMB)
library(DHARMa)
library(emmeans)
library(car)

find("ggscatter")

```

```{r}
class(data)