---
title: "Chap1 r and social levels"
output: html_document
---

##[comment]Provide a summary of your data (means, variation, etc.) on association (e.g., pairs, families, extended families, colonies), number and size of groups, and social network metrics, before delving into models that test why you see these patterns. 

```{r}
aso_ssa_mf <- aso_ssa %>% 
  filter(V12sex == "mf") %>% 
  mutate(vm = ifelse(V1sex=="m", id1, id2), #rearrange V1 male and V2 female
         vf = ifelse(V2sex=="f", id2, id1)) %>% 
  mutate(id1=vm, id2=vf) %>% 
  select(-vm, -vf, -V1sex, -V2sex) %>% 
  rename(aso = association) %>% setDT()
```


#Tidy data
##PAIR
```{r}
paird <- pair_mf %>%  
  select(year, plot, V1, V2, V12sex, r) %>% 
  left_join(aso_ssa_mf[gtype=="daytime", .(year, id1, id2, aso)], by=c("year", "V1"="id1", "V2"="id2")) %>% 
  filter(!is.na(aso)) #ORKM/OYPM bad data

sum_pair_yearplot <-  paird %>% 
  group_by(year, plot) %>%
  summarise(rMean = mean(r), asoMean = mean(aso), 
            rSD = sd(r), asoSD = sd(aso))

sum_pair_year <- paird %>% 
  group_by(year) %>%
  summarise(rMean = mean(r), asoMean = mean(aso),
            rSD = sd(r), asoSD = sd(aso))

#one pair is only calculated once, association is averaged across years
sum_pair <- paird %>% 
  group_by(V1, V2) %>% 
  summarise(r = mean(r), aso = mean(aso))  #summarise by pair

sum_pair_all <- sum_pair %>% ungroup() %>% 
  summarise(n = nrow(.),
            rMean = mean(r), asoMean = mean(aso), 
            rSD = sd(r), asoSD = sd(aso))
  
#write_xlsx(sum_pair, "../output/r and social levels/data/output_pair_raso.xlsx")
#write_xlsx(sum_pair_all, "../output/r and social levels/data/output_pair_raso_all.xlsx")
```

#social groups
```{r}
levels(mygroup_ssa_r$V12sex) <- c("mm","ff","mf")

#by $groupid
sum_mygroup <- mygroup_ssa_r %>% 
  filter(V1!="MYPO"&V2!="MYPO") %>% 
  group_by(year, plot, gtype, groupid) %>% 
  summarise(r = mean(r), aso = mean(association))

sum_mygroup_year <- sum_mygroup %>% 
  group_by(year, gtype) %>% 
  summarise(rMean = mean(r), asoMean = mean(aso),
            rSD = sd(r), asoSD = sd(aso))

sum_mygroup_yearplot <- sum_mygroup %>% 
  group_by(year, plot, gtype) %>% 
  summarise(rMean = mean(r), asoMean = mean(aso),
            rSD = sd(r), asoSD = sd(aso))

sum_mygroup_gtype <- sum_mygroup %>% 
  group_by(gtype) %>% 
  summarise(n = n(),
            rMean = mean(r), asoMean = mean(aso),
            rSD = sd(r), asoSD = sd(aso))

#write_xlsx(sum_mygroup, "../output/r and social levels/data/output_mygroup_raso.xlsx")
#write_xlsx(sum_mygroup_gtype, "../output/r and social levels/data/output_mygroup_raso_bygtype.xlsx")
```



#social groups by sex (This is good)
```{r}
sum_mygroup_sex <- mygroup_ssa_r %>% 
  filter(V1!="MYPO"&V2!="MYPO") %>% 
  group_by(year, plot, gtype, groupid, V12sex) %>% 
  summarise(r = mean(r), aso = mean(association)) %>% 
  mutate(V12sex = ordered(V12sex, levels = c("mm", "ff", "mf"))) %>% setDT()

sum_mygroup_sex_all <- sum_mygroup_sex %>%  
  group_by(gtype, V12sex) %>% 
  summarise(rMean = mean(r), asoMean = mean(aso), 
            rSD = sd(r), asoSD=sd(aso))

#write_xlsx(sum_mygroup_sex, "../output/r and social levels/data/output_mygroup_raso_bysex.xlsx")
#write_xlsx(sum_mygroup_sex_all, "../output/r and social levels/data/output_mygroup_raso_bysex_all.xlsx")
```

#social groups by sex and non-pair MF
```{r}
sum_mygroup_sex_np <- mygroup_ssa_r %>% 
  filter(V1!="MYPO"&V2!="MYPO"&pair==0) %>% 
  group_by(gtype, groupid, V12sex) %>% 
  summarise(r = mean(r), aso = mean(association)) %>% 
  mutate(V12sex = ordered(V12sex, levels = c("mm", "ff", "mf")))

sum_mygroup_sex_np_all <- sum_mygroup_sex %>%  
  group_by(gtype, V12sex) %>% 
  summarise(rMean = mean(r), asoMean = mean(aso), 
            rSD = sd(r), asoSD=sd(aso))

#write_xlsx(sum_mygroup_sex_np, "../output/r and social levels/data/output_mygroup_raso_bysex_np.xlsx")
#write_xlsx(sum_mygroup_sex_np_all, "../output/r and social levels/data/output_mygroup_raso_bysex_all_np.xlsx")
```

#pair aso withint social groups
```{r}
sum_mygroup_pair_year <- mygroup_ssa_r %>% 
  filter(V1!="MYPO"&V2!="MYPO"&pair==1) %>% 
  group_by(year, plot, gtype) %>% 
  summarise(rMean = mean(r), asoMean = mean(association), 
            rSD = sd(r), asoSD=sd(association))

view(sum_mygroup_pair)

sum_mygroup_pair <- mygroup_ssa_r %>% 
  filter(V1!="MYPO"&V2!="MYPO"&pair==1) %>% 
  group_by(gtype) %>% 
  summarise(rMean = mean(r), asoMean = mean(association), 
            rSD = sd(r), asoSD=sd(association))

view(sum_mygroup_pair)

 #write_xlsx(sum_mygroup_pair_year, "../output/r and social levels/data/output_mygroup_aso_pair_year.xlsx")
 #write_xlsx(sum_mygroup_pair, "../output/r and social levels/data/output_mygroup_aso_pair.xlsx")
```

#GROUPS
#Stats test for r/sex within groups
#GLMER 
```{r}
library(glmmTMB)
library(emmeans)
source("overdisp_fun.R")

df <- sum_mygroup_sex %>% 
  filter(V12sex != "mf") %>% 
  left_join(mygroup_ssa_gs, by=c("year","plot","gtype","groupid")) %>% 
  mutate(V12sex = factor(V12sex, levels = c("ff", "mm"))) %>%
  mutate(gtype = factor(gtype, levels = c("daytime", "sleeping", "breeding")))

#full model, first and second order----
fit <- glmmTMB(r ~ V12sex*gtype + gs + (1|year) + (1|plot) + (1|groupid), family = gaussian,  data=df)

#diagnostic: ok
hist(resid(fit))

summary(fit)
glmmTMB:::Anova.glmmTMB(fit)

emm.fit <- emmeans(fit, pairwise ~ V12sex*gtype, type = "response")
print(emm.fit)
plot(emm.fit)

ggsave("../output/r and social levels/fig/fig_emmeans_mmff_r_gtype.png")
```


#Stats test for aso/sex within groups
#GLMER 
```{r}
library(glmmTMB)
library(emmeans)
source("overdisp_fun.R")

df1 <- df %>% mutate(aso = replace(aso, aso==1, 0.999)) #modify for zero-inflated beta regression

#full model, first and second order----
fit.aso <- glmmTMB(aso ~ V12sex*gtype + gs + (1|year) + (1|plot) + (1|groupid), ziformula =~ 1, family=beta_family(link="logit"),  data=df1)

#diagnostic: ok
resd <- DHARMa::simulateResiduals(fit)  #simulation output
plot(resd)

summary(fit.aso)
glmmTMB:::Anova.glmmTMB(fit.aso)

emm.fit.aso <- emmeans(fit.aso, pairwise ~ V12sex*gtype, type = "response")
print(emm.fit.aso)
plot(emm.fit.aso)

ggsave("../output/r and social levels/fig/fig_emmeans_mmff_aso_gtype.png")
```

#GLMER : with oly daytime and nighttime groups
```{r}
library(glmmTMB)
library(emmeans)
source("overdisp_fun.R")

df.D <- df %>% 
  mutate(aso = replace(aso, aso==1, 0.999)) %>%
  filter(gtype == "daytime") #modify for zero-inflated beta regression

#full model, first and second order----
fit.aso2 <- glmmTMB(aso ~ V12sex + gs + (1|year) + (1|plot) + (1|groupid), ziformula =~ 1, family=beta_family(link="logit"),  data=df.D)

#diagnostic: ok
resd <- DHARMa::simulateResiduals(fit.aso2)  #simulation output
plot(resd)

summary(fit.aso2)
glmmTMB:::Anova.glmmTMB(fit.aso2)

emm.fit.aso <- emmeans(fit.aso2, pairwise ~ V12sex*gtype, type = "response")
print(emm.fit.aso2)
plot(emm.fit.aso2)

ggsave("../output/r and social levels/fig/fig_emmeans_mmff_asoD_gtype.png")
```

```{r}
df.N <- df %>% 
  mutate(aso = replace(aso, aso==1, 0.999)) %>%
  filter(gtype == "sleeping") #modify for zero-inflated beta regression

#full model, first and second order----
fit.aso3 <- glmmTMB(aso ~ V12sex + gs + (1|year) + (1|plot) + (1|groupid), ziformula =~ 1, family=beta_family(link="logit"),  data=df.N)

#diagnostic: ok
resd <- DHARMa::simulateResiduals(fit.aso3)  #simulation output
plot(resd)

summary(fit.aso3)
glmmTMB:::Anova.glmmTMB(fit.aso3)

emm.fit.aso <- emmeans(fit.aso3, pairwise ~ V12sex*gtype, type = "response")
print(emm.fit.aso3)
plot(emm.fit.aso3)

ggsave("../output/r and social levels/fig/fig_emmeans_mmff_asoN_gtype.png")
```


##COLONY
```{r}
colony_dyad <- colony_member_main %>%
  filter(color != "MYPO") %>% #no genetic data
  select(year, plot, colony, color) %>% 
  add_count(year, plot, colony) %>% 
  filter(n>1) %>% 
  group_by(year, plot, colony) %>% 
  group_modify(., ~ as.data.frame.matrix(t(combn(.$color, 2)), stringsAsFactors = F)) %>%
  as.data.table() %>% 
  mutate(V12sex = fun_sexdyad(.[,.(V1,V2)], sex)[[3]],
         r = fun_r(.[,.(V1,V2)], relate), 
         aso = fun_weight(.[,.(V1,V2)], aso_ssa[gtype=="daytime"], "association"),
         asoN = fun_weight(.[,.(V1,V2)], aso_ssa[gtype=="sleeping"], "association")) %>% 
  mutate(aso = replace_na(aso, 0)) %>% #aso=NA means they never appeared in the daytime
  mutate(V12sex = ordered(V12sex, levels=c("mm", "ff", "mf"))) %>% 
  left_join(select(colony_size, year, colony, n_birds, size), by=c("year", "colony")) %>% 
  mutate(log_nbirds = log(n_birds)) %>% 
  setDT()

sum_colony <- colony_dyad %>% 
  group_by(year, plot, colony) %>% 
  summarise(r = mean(r), aso = mean(aso), rSD = sd(r))

sum_colony_yearplot <- sum_colony %>%
  group_by(year, plot) %>% 
  summarise(rMean = mean(r), asoMean = mean(aso),
            rSD = sd(r), asoSD = sd(aso))

sum_colony_year <- sum_colony %>% 
  group_by(year) %>% 
  summarise(rMean = mean(r), asoMean = mean(aso),
            rSD = sd(r), asoSD = sd(aso)) 

sum_colony_plot <- sum_colony %>% 
  group_by(plot) %>% 
  summarise(rMean = mean(r), asoMean = mean(aso),
            rSD = sd(r), asoSD = sd(aso)) 

sum_colony_all <- sum_colony %>% 
  ungroup() %>% 
  summarise(n = nrow(.),
            rMean = mean(r), asoMean = mean(aso),
            rSD = sd(r), asoSD = sd(aso))

#by sex
sum_colony_sex <- colony_dyad %>%
  group_by(year, plot, colony, V12sex) %>% 
  summarise(r = mean(r), aso = mean(aso), asoN = mean(asoN)) %>% setDT()

sum_colony_sex2 <- colony_dyad %>%
  group_by(year, plot, colony, V12sex) %>% 
  summarise(rMean = mean(r), asoMean = mean(aso), asoNMean = mean(asoN), rSD = sd(r)) %>% setDT()

sum_colony_sex_all <- sum_colony_sex %>% 
  group_by(V12sex) %>% 
  summarise(rMean = mean(r), asoMean = mean(aso),
            rSD = sd(r), asoSD = sd(aso))

#by colony size
sum_colony_size <- colony_dyad %>%
  group_by(year, plot, colony, size, V12sex) %>% 
  summarise(r = mean(r), aso = mean(aso)) %>% setDT()

sum_colony_size_all <- sum_colony_size %>%
  group_by(size, V12sex) %>% 
  summarise(rMean = mean(r), rSD = sd(r), aso = mean(aso)) %>% setDT()

#write_xlsx(sum_colony_all, "../output/r and social levels/data/output_colony_raso_all.xlsx")
#write_xlsx(sum_colony_sex_all, "../output/r and social levels/data/output_colony_raso_all_bysex.xlsx")
  
```

#Tidy table for output
```{r}
#colony
sum_colony_sex_w <- sum_colony_sex %>% 
  pivot_wider(., names_from = )
```


#Stats test for r/sex within colony
#GLMER 
```{r}
library(glmmTMB)
library(emmeans)
source("overdisp_fun.R")

dfc <- sum_colony_sex %>% 
  filter(V12sex != "mf") %>% 
  left_join(colony_size, by=c("year","plot","colony")) %>% 
  mutate(yearcolony = paste0(year, colony)) %>% 
  mutate(V12sex = factor(V12sex, levels = c("ff", "mm"))) %>% 
  mutate(size2 = factor(size, levels = c("S", "M", "L", "XL")))
```

#relatedness ~ sex, within colonies
```{r}
#full model, first and second order----
fitc <- glmmTMB(r ~ V12sex + scale(n_birds) + (1|year) + (1|plot) + (1|colony), family = "gaussian",  data=dfc)

#diagnostic: ok
hist(resid(fitc))

summary(fitc)
glmmTMB:::Anova.glmmTMB(fitc)

emm.fitc <- emmeans(fitc, pairwise ~ V12sex*size2, type = "response")
print(emm.fitc)
plot(emm.fitc)

ggsave("../output/r and social levels/fig/fig_emmeans_mmff_r_colony.png")
```

#Stats test for DAYTIME aso/sex within colonies
#GLMER 
```{r}
library(glmmTMB)
library(emmeans)
source("overdisp_fun.R")

#full model, first and second order----
fitc.aso <- glmmTMB(aso ~ V12sex + scale(n_birds) + (1|year) + (1|plot) + (1|colony), ziformula =~ 1, family=beta_family(link="logit"),  data=dfc)

#diagnostic: ok
resd <- DHARMa::simulateResiduals(fitc.aso)  #simulation output
plot(resd)

summary(fitc.aso)
glmmTMB:::Anova.glmmTMB(fitc.aso)

emm.fitc.aso <- emmeans(fitc.aso, pairwise ~ V12sex*size2, type = "response")
print(emm.fitc.aso)
plot(emm.fitc.aso)

ggsave("../output/r and social levels/fig/fig_emmeans_mmff_aso_colony.png")
```

#aso~sex, colony, NIGHTTIME
```{r}
dfc.N <- dfc %>% mutate(asoN = replace(aso, aso==1, 0.999))

fitc.aso2 <- glmmTMB(asoN ~ V12sex*scale(n_birds) + (1|year) + (1|plot) + (1|colony), ziformula =~ 1, family=beta_family(link="logit"),  data=dfc.N)

summary(fitc.aso2)
glmmTMB:::Anova.glmmTMB(fitc.aso2)
```

#-------r, sex and colony size---------
```{r}
#tidy data for modeling
#[sum_r_colony_allbirds]----
sum_r_colony_allbirds <- colony_dyad %>% 
  group_by(year, plot, colony) %>% 
  summarise(mean = mean(r)) %>% 
  left_join(select(colony_size, year, colony, n_birds), by=c("year", "colony")) %>% 
  mutate(log_nbirds = log(n_birds)) %>% 
  setDT()

#[sum_r_colony_bysex]----
sum_r_colony_bysex <- colony_dyad %>% 
  group_by(year, plot, colony, size, V12sex) %>% 
  summarise(mean = mean(r)) %>% 
  left_join(select(colony_size, year, colony, n_birds), by=c("year", "colony")) %>% 
  mutate(log_nbirds = log(n_birds)) %>% 
  setDT()

#[sum_r_colony_bysexsize]----
sum_r_colony_bysexsize <- colony_dyad %>% 
  left_join(select(colony_size, year, colony, n_birds), by=c("year", "colony")) %>% 
  group_by(size, V12sex) %>% 
  summarise(mean = mean(r), sd = sd(r)) %>% 
  setDT()
```

#plot r and colony size (results for DR)
```{r}
ggscatter(colony_dyad, x = "log_nbirds", y = "r", facet.by = c("V12sex"),
          size = 1, 
          add = "reg.line", conf.int = T, 
          add.params = list(color = "red",
                            fill = "lightgray"), 
          xlab="Number of birds (log)")

# log_nbirds
ggscatter(sum_r_colony_bysex, x = "log_nbirds", y = "mean", facet.by = c("V12sex"),
          size = 1, 
          add = "reg.line", conf.int = T, 
          add.params = list(color = "red",
                            fill = "lightgray"), 
          xlab="Number of birds in the colony (Ln)", 
          ylab="Mean relatedness")

#ggsave("../output/r and social levels/fig/fig_colony size and r.png", width=5, height=2.5)

#
ggscatter(sum_r_colony_allbirds, x = "log_nbirds", y = "mean",
          size = 1, 
          add = "reg.line", conf.int = T, 
          add.params = list(color = "red",
                            fill = "lightgray"), 
          xlab="Number of birds in the colony (Ln)", 
          ylab="Mean relatedness") 

#ggsave("../output/r and social levels/fig/fig_colony size and r_all birds.png", width=7, height=4)
```


#stats on r and colony size
```{r}
#tidy data
sum_r_colony$V12sex <- factor(sum_r_colony$V12sex)
sum_r_colony$year <- factor(sum_r_colony$year)

#ALL birds
fit0 <- lmer(mean ~ log_nbirds + (1|plot), data = sum_r_colony_allbirds)

summary(fit0)

#-----------average by sex------------------#
#colony size as continuous , interaction sig.
fit <- lmer(mean ~ log_nbirds*V12sex + year + (1|plot), data = sum_r_colony)

anova(fit)
summary(fit)

#------now separate sex--------#
#by sex, mm
fit <- lmer(mean ~ log_nbirds + year + (1|plot), data = sum_r_colony[V12sex=="mm"])

anova(fit)
summary(fit)
hist(resid(fit)) #so good

#by sex, mf
fit <- lmer(mean ~ log_nbirds + year + (1|plot), data = sum_r_colony[V12sex=="mf"])

anova(fit)
summary(fit)
hist(resid(fit)) #so good

#by sex, ff
fit <- lmer(mean ~ log_nbirds + year + (1|plot), data = sum_r_colony[V12sex=="ff"])

anova(fit)
summary(fit)
hist(resid(fit)) #so good

#-------without year--------#
#by sex, ff; singular problem
fit <- lmer(mean ~ log_nbirds + (1|plot), data = sum_r_colony[V12sex=="ff"])

```

##SITE (all birds appeared on site are included)
```{r}
site_dyad <- data %>% 
  filter(color != "MYPO") %>% #no genetic data
  select(year, plot, color) %>%
  distinct() %>% 
  left_join(select(age, color, year, age), by=c("year", "color")) %>% 
  filter(age!="IM") %>% 
  group_by(year, plot) %>% 
  group_modify(., ~ as.data.frame.matrix(t(combn(.$color, 2)), stringsAsFactors = F)) %>%
  as.data.table() %>% 
  mutate(V12sex = fun_sexdyad(.[,.(V1,V2)], sex)[[3]],
         r = fun_r(.[,.(V1,V2)], relate), 
         aso = fun_weight(.[,.(V1,V2)], aso_ssa[gtype=="daytime"], "association")) %>% 
  mutate(aso = replace_na(aso, 0)) %>% #aso=NA means they never appeared in the daytime
  mutate(V12sex = ordered(V12sex, levels=c("mm", "ff", "mf"))) %>% 
  left_join(select(pair, year, V1, V2, pair), by = c("year", "V1", "V2")) %>% 
  left_join(select(colony_member_main1, year, plot, colony, color), by=c("year", "plot", "V1"="color")) %>% 
  left_join(select(colony_member_main1, year, plot, colony, color), by=c("year", "plot", "V2"="color"), suffix = c("1", "2")) %>% 
  mutate(samecolony = ifelse(colony1==colony2, 1, 0)) %>% 
  left_join(mygroup_ssa[gtype=="daytime", .(id, year, plot, groupid)], by=c("year", "plot", "V1"="id")) %>% 
  left_join(mygroup_ssa[gtype=="daytime", .(id, year, plot, groupid)], by=c("year", "plot", "V2"="id"), suffix=c("1", "2")) %>%  
  mutate(samegroup = ifelse(groupid1==groupid2, 1, 0)) %>% 
  setDT()

#saveRDS(site_dyad, "../output/r and social levels/data/output_site_dyad_raso.rdata")
```

#summary for site level
```{r}
##samecolony
sum_site_yearplot <- site_dyad %>% 
  group_by(year, plot) %>% 
  summarise(r = mean(r), aso = mean(aso))

sum_site_plot <- sum_site_yearplot %>% 
  group_by(plot) %>% 
  summarise(r = mean(r), aso = mean(aso))

sum_site_all <- site_dyad %>% 
  group_by(samecolony) %>% 
  summarise(n = nrow(.),
            rMean = mean(r), asoMean = mean(aso),
            rSD = sd(r), asoSD = sd(aso))

#samegroup
sum_site_gr <- site_dyad %>%
  filter(!is.na(samegroup)) %>% 
  group_by(samecolony, samegroup) %>% 
  summarise(r = mean(r), aso = mean(aso))

#by sex
sum_site_sex <- site_dyad %>%
  group_by(plot, V12sex) %>% 
  summarise(rMean = mean(r), asoMean = mean(aso), 
            rSD = sd(r), asoSD = sd(aso))

sum_site_sex_yearplot <- site_dyad %>%
  group_by(plot, year, V12sex) %>% 
  summarise(rMean = mean(r), asoMean = mean(aso), 
            rSD = sd(r), asoSD = sd(aso))

sum_site_sex_plot <- sum_site_sex_yearplot %>%
  group_by(plot, V12sex) %>% 
  summarise(rmean = mean(rMean), asomean = mean(asoMean), 
            rsd = sd(rSD), asosd = sd(asoSD))

#write_xlsx(sum_site_sex, "../output/r and social levels/data/output_site_r_sex.xlsx")
```

#r and sex by plot; MCMCglmm-multimembership
```{r}
library(MCMCglmm)
library(car)
library(coda)
library(beepr)

source("vif_MCMCglmm.R") #vif.MCMCglmm
```

```{r}
#[df]----
#only mm, ff
df <- site_dyad %>% 
  filter(V12sex != "mf") %>% 
  select(V1, V2, year, plot, r, V12sex) %>% setDT()

#summarise sample size
data.frame(color = c(df$V1, df$V2)) %>% distinct() %>% mutate(sex = fun_sex(.$color, sex)) %>% group_by(sex) %>% summarise(n = n())
data.frame(color = c(df[plot=="MSTO"]$V1, df[plot=="MSTO"]$V2)) %>% distinct() %>% mutate(sex = fun_sex(.$color, sex)) %>% group_by(sex) %>% summarise(n = n())
data.frame(color = c(df[plot=="SPRA"]$V1, df[plot=="SPRA"]$V2)) %>% distinct() %>% mutate(sex = fun_sex(.$color, sex)) %>% group_by(sex) %>% summarise(n = n())
data.frame(color = c(df[plot=="LLOD"]$V1, df[plot=="LLOD"]$V2)) %>% distinct() %>% mutate(sex = fun_sex(.$color, sex)) %>% group_by(sex) %>% summarise(n = n())

```

#multi-membership MCMCglmm
```{r}
df <- df %>% 
  mutate(V1 = as.factor(V1), V2 = as.factor(V2), V12sex=factor(V12sex, levels = c("ff", "mm"))) %>% 
  setDT()

#prepare for multi-membership 
df$V1 <- as.factor(c(levels(df$V2),as.character(df$V1)))[-(1:length(levels(df$V2)))] 
df$V2 <- as.factor(c(levels(df$V1),as.character(df$V2)))[-(1:length(levels(df$V1)))]

priors1<- list(R = list(V = 1, nu = 0.002), G = list(G1 = list(V =1, nu = 0.002))) #uninformative prior

mcmcfit <- MCMCglmm(r ~ V12sex*plot, random = ~ mm(V1 + V2), family = "gaussian", data = df, verbose = FALSE, prior=priors1, nitt = 65000, thin = 50, burnin = 15000)

#check graph
plot(mcmcfit$VCV)
autocorr(mcmcfit$VCV)

summary(mcmcfit)$solutions
posterior.mode(mcmcfit$VCV) #randome effect; sig. meaning dyadID are imporant, prob. due to kinship
HPDinterval(mcmcfit$VCV)

saveRDS(mcmcfit, "../output/r and social levels/data/mcmcfit.rdata")
```

#test MM and FF r for only inds r >= 0.25
```{r}
df25 <- site_dyad %>% 
  filter(V12sex != "mf" & r>=0.25) %>% 
  select(V1, V2, year, plot, r, V12sex) %>% 
  mutate(V1=as.factor(V1), V2=as.factor(V2), V12sex=factor(V12sex, levels = c("mm", "ff")))

#prepare for multi-membership 
df25$V1 <- as.factor(c(levels(df25$V2),as.character(df25$V1)))[-(1:length(levels(df25$V2)))] 
df25$V2 <- as.factor(c(levels(df25$V1),as.character(df25$V2)))[-(1:length(levels(df25$V1)))]

```

#test MM and FF r for only inds r >= 0.25
```{r}
priors1<- list(R = list(V = 1, nu = 0.002), G = list(G1 = list(V =1, nu = 0.002))) #uninformative prior

mcmcfit2 <- MCMCglmm(r ~ V12sex*plot, random = ~ idv(mult.memb(~ V1 + V2)), family = "gaussian", data = df25, verbose = FALSE, prior=priors1)

#check graph
plot(mcmcfit2$VCV)
plot(mcmcfit2$Sol)

autocorr.diag(mcmcfit2$VCV)
autocorr.diag(mcmcfit2$Sol)

summary(mcmcfit2)$solutions

saveRDS(mcmcfit2, "../output/r and social levels/data/mcmcfit.rdata")
```

#multi-membership MCMCglmm
#r within groups
```{r}
dfg <- mygroup_ssa_r %>% 
  mutate(dyadID = paste0(V1, V2)) %>% 
  filter(V12sex != "mf" & V1 != "MYPO" & V2 != "MYPO") %>% 
  mutate(V12sex = factor(V12sex, levels = c("ff", "mm"))) %>%
  mutate(gtype = factor(gtype, levels = c("daytime", "sleeping", "breeding"))) %>% 
  mutate(V1 = as.factor(V1), V2 = as.factor(V2), V12sex=factor(V12sex, levels = c("ff", "mm"))) %>% 
  setDT()
```

```{r}
#prepare for multi-membership 
dfg$V1 <- as.factor(c(levels(dfg$V2),as.character(dfg$V1)))[-(1:length(levels(dfg$V2)))] 
dfg$V2 <- as.factor(c(levels(dfg$V1),as.character(dfg$V2)))[-(1:length(levels(dfg$V1)))]

priors1<- list(R = list(V = 1, nu = 0.002), G = list(G1 = list(V =1, nu = 0.002), G1 = list(V =1, nu = 0.002))) #uninformative prior

mcmcfit.g <- MCMCglmm(r ~ V12sex*gtype + gs, random = ~ mm(V1 + V2) + groupid, family = "gaussian", data = dfg, verbose = FALSE, prior = priors1) #nitt = 65000, thin = 50, burnin = 15000

#not much diff. between gtype

#check graph
plot(mcmcfit.g$VCV)
autocorr(mcmcfit.g$VCV)

summary(mcmcfit.g)

saveRDS(mcmcfit.g, "../output/r and social levels/data/mcmcfit.g.rdata")
```

#r ~ sex, MCMCglmm, Daytime
#Results are no different from using group data and GLMM, even more sig!!
```{r}
dfg.D <- dfg %>% filter(gtype == "daytime")

#prepare for multi-membership 
dfg.D$V1 <- as.factor(c(levels(dfg.D$V2),as.character(dfg.D$V1)))[-(1:length(levels(dfg.D$V2)))] 
dfg.D$V2 <- as.factor(c(levels(dfg.D$V1),as.character(dfg.D$V2)))[-(1:length(levels(dfg.D$V1)))]

priors1<- list(R = list(V = 1, nu = 0.002), G = list(G1 = list(V =1, nu = 0.002), G1 = list(V =1, nu = 0.002))) #uninformative prior

mcmcfit.gD <- MCMCglmm(r ~ V12sex + gs, random = ~ mm(V1 + V2) + groupid, family = "gaussian", data = dfg.D, verbose = FALSE, prior = priors1) #nitt = 65000, thin = 50, burnin = 15000

#check graph
plot(mcmcfit.gD$VCV)
plot(mcmcfit.gD$Sol)
autocorr(mcmcfit.gD$VCV)

summary(mcmcfit.gD)

saveRDS(mcmcfit.gD, "../output/r and social levels/data/mcmcfit.gD.rdata")
```

#r ~ sex, MCMCglmm, Nighttime
```{r}
dfg.N <- dfg %>% filter(gtype == "sleeping")

#prepare for multi-membership 
dfg.N$V1 <- as.factor(c(levels(dfg.N$V2),as.character(dfg.N$V1)))[-(1:length(levels(dfg.N$V2)))] 
dfg.N$V2 <- as.factor(c(levels(dfg.N$V1),as.character(dfg.N$V2)))[-(1:length(levels(dfg.N$V1)))]

priors1<- list(R = list(V = 1, nu = 0.002), G = list(G1 = list(V =1, nu = 0.002), G2 = list(V =1, nu = 0.002), G3 = list(V =1, nu = 0.002), G4 = list(V =1, nu = 0.002), G5 = list(V =1, nu = 0.002))) #uninformative prior

mcmcfit.gN <- MCMCglmm(r ~ V12sex + gs, random = ~ mm(V1 + V2) + dyadID + groupid + year + plot, family = "gaussian", data = dfg.N, verbose = FALSE, prior = priors1) #nitt = 65000, thin = 50, burnin = 15000

#check graph
plot(mcmcfit.gN$VCV)
plot(mcmcfit.gN$Sol)
autocorr(mcmcfit.gN$VCV)

summary(mcmcfit.gD)

saveRDS(mcmcfit.gD, "../output/r and social levels/data/mcmcfit.gD.rdata")
```
