---
title: "Chap1 spatial organization"
output: html_document
---

```{r}
#[nestdist]nest distance for all colonyXyear
#[tree_hei]tree height and size
#[sum_sleepnest]inds for all nests by colonyXyear
#[first_mf][m][f]nest representative
#[combo_m][combo_f]nest and owner combo with distance and r, repeated
#[df_m_nested][df_f_nested]

#[unicombo_m]combo only appeared once
```


##import data
```{r}
#[nestdist.ls]----
#nest distance matrix by colony
nestdist.ls <- readRDS("../data/2013-2017 weaver nest dist_matrix.RData")

#[tree_hei]----
#tree height
tree_hei <- read_xlsx("../data/c_2013-2017 weaver colony measurement.xlsx") %>% 
  mutate(year=as.character(year)) %>% 
  mutate(height_m = height/100, 
         size_hei = if_else(height >=300, "L", "S"))  #if cut at 250cm, too few small colonies
```

#Let'e look at the tree height
```{r}
gghistogram(tree_hei, x="height", y="..count..")

```

#You can jump to Line 198 for analysis
## tidy nest distance data
```{r}
#convert nest distance matrix to df
f <- function(x){
  output <- x %>% modify_if(upper.tri(., diag = F), ~NA) %>% 
    melt(., na.rm = T) %>% 
    mutate_if(., is.integer, as.character)
  return(output)
}

nestdist_df.ls <- lapply(nestdist.ls, f)


#[nestdist]----
#nest distance df by yearXcolony
nestdist <- do.call(rbind, nestdist_df.ls) %>% 
  rownames_to_column("rowname") %>%
  mutate(year = substr(rowname, 1, 4), colony = substr(rowname, 5, 10)) %>% 
  rename(nest1=Var1, nest2=Var2, dist=value) %>% 
  mutate(dist_m = dist/100) %>%
  group_by(year, colony) %>% 
  mutate(dist_z = scale(dist_m)) %>% #by year and colony
  dplyr::select(-rowname) %>% 
  mutate(id12 = paste0(nest1, nest2), 
         id21 = paste0(nest2, nest1)) %>% 
  as.data.table()

#write_xlsx(nestdist, "../output/spatial_arrange/data/output_nestdist.xlsx")

```


## finding households
```{r}
#[sum_sleepnest]----
sum_sleepnest <- sleepnest %>% 
  left_join(sum_sampledays_bynest, by=c("year","plot", "colony", "nest")) %>%
  rename(n_testerdays = n) %>% 
  group_by(year, colony, nest,  n_testerdays) %>% 
  mutate(n_sampling = length(unique(sleep_date))) %>% #$n_sampling:# of sampling nights for nest, this is ONLY the # of nights birds were present, not the real sampling nights
  group_by(year, colony, nest, color, n_testerdays, n_sampling) %>% 
  summarise(n_nights = n()) %>% #$n_nights: # of nights in the nest
  mutate(per_nights = round(n_nights/n_sampling, 2)) %>% 
  mutate(sex = fun_sex(color, sex)) %>% 
  group_by(year, colony, nest, sex) %>% 
  arrange(-n_nights, .by_group=T) %>% 
  mutate(order_sex = row_number()) %>% 
  mutate(plot = substr(colony, 1, 4)) %>% 
  dplyr::select(year, plot, colony, everything ()) %>% 
  setDT()

#[first_mf]----
#each ind has only ONE nest
first_mf <- sum_sleepnest %>% #n=495
  filter(n_nights>=3 & order_sex == 1) %>% 
  group_by(year, colony, color) %>% #$color
  arrange(-n_nights,.by_group=T) %>% 
  slice(1) %>% #chose ONLY the dominant nest birds maintained
  select(year, plot, colony, nest, color, sex) %>% 
  pivot_wider(., names_from = "sex", values_from = "color") %>% 
  as.data.table() %>% 
  setDT()

write_xlsx(first_mf, "../output/spatial_arrange/data/output_first_mf.xlsx")

#[m][f]----
m <- first_mf %>% select(-f) %>% filter(!is.na(m)) %>% 
  add_count(year, colony) %>%
  filter(n>=3) %>% select(-n) #colony size>=3males
f <- first_mf %>% select(-m) %>% filter(!is.na(f)) %>% 
  add_count(year, colony) %>%
  filter(n>=3) %>% select(-n) #colony size>=3females
```

#make combinations of nest and m1, add $r and $dist
```{r}
#this is repeated combo
#[combo_m]----
combo_m <- m %>% 
  group_by(year, plot, colony) %>% 
  group_modify(., ~ expand.grid(.$nest, .$nest, KEEP.OUT.ATTRS = F, stringsAsFactors = F)) %>%    #create combination of nests, n=4867
  rename("nest1" = "Var1", "nest2" = "Var2") %>% 
  left_join(m, by=c("year","plot","colony","nest1"="nest")) %>% 
  left_join(m, by=c("year","plot","colony","nest2"="nest"), suffix=c("1", "2")) %>%
  as.data.table() %>% 
  mutate(dist_m = fun_weight(.[,.(nest1, nest2)], nestdist, "dist_m"), 
         dist_z = fun_weight(.[,.(nest1, nest2)], nestdist, "dist_z"), 
         r = fun_weight(.[,.(m1, m2)],relate, "r"), 
         kinship = fun_kinship(.[,.(m1, m2)], kinship, "kinorder")) %>% 
  mutate(kinship = ordered(kinship, levels = c("first", "second", "UR"))) %>%
  mutate(r = replace_na(r, 1)) %>% 
  left_join(mygroup_ssa[gtype=="daytime",.(year, plot, id, groupid)], by=c("year", "plot", "m1"="id")) %>% 
  left_join(mygroup_ssa[gtype=="daytime",.(year, plot, id, groupid)], by=c("year", "plot", "m2"="id"), suffix-c("_1","_2")) %>% 
  mutate(samegroup = as.factor(ifelse(groupid.x == groupid.y, 1, 0))) %>% 
  mutate(samegroup = ordered(samegroup, levels=c("1","0"))) %>% 
  setDT()

#[combo_f]----
combo_f <- f %>% 
  group_by(year, plot, colony) %>% 
  group_modify(., ~ expand.grid(.$nest, .$nest, KEEP.OUT.ATTRS = F, stringsAsFactors = F)) %>%    #create combination of nests, n=4867
  rename("nest1" = "Var1", "nest2" = "Var2") %>% 
  left_join(f, by=c("year","plot","colony","nest1"="nest")) %>% 
  left_join(f, by=c("year","plot","colony","nest2"="nest"), suffix=c("1","2")) %>% 
  as.data.table() %>% 
  mutate(dist_m = fun_weight(.[,.(nest1, nest2)],nestdist, "dist_m"), 
         dist_z = fun_weight(.[,.(nest1, nest2)], nestdist, "dist_z"), 
         r = fun_weight(.[,.(f1, f2)],relate, "r"),
         kinship = fun_kinship(.[,.(f1, f2)], kinship, "kinorder")) %>% 
  mutate(kinship = ordered(kinship, levels = c("first", "second", "UR"))) %>%
  mutate(r = replace_na(r, 1)) %>% 
  left_join(mygroup_ssa[gtype=="daytime",.(year, plot, id, groupid)], by=c("year", "plot", "f1"="id")) %>% 
  left_join(mygroup_ssa[gtype=="daytime",.(year, plot, id, groupid)], by=c("year", "plot", "f2"="id"), suffix-c("_1","_2")) %>% 
  mutate(samegroup = as.factor(ifelse(groupid.x == groupid.y, 1, 0))) %>%
  mutate(samegroup = ordered(samegroup, levels=c("1","0"))) %>% 
  setDT()
  
```




```{r}
#convert data to matrix
fun_dtm <- function(data, id1, id2, var){
  x <- data %>% 
    dplyr::select(id1, id2, var) %>% 
    spread(key = id2, value = var) %>% 
    column_to_rownames(., var = id1) %>% 
    as.matrix()
  return(x)
}
```

##Into nested data mode
```{r}
#[df_m_nested]----
df_m_nested <- combo_m %>%
  group_by(year, plot, colony) %>% 
  nest() %>% 
  mutate(dist.m = map(data, fun_dtm, "nest1", "nest2", "dist_m")) %>%
  mutate(distz.m = map(data, fun_dtm, "nest1", "nest2", "dist_z")) %>%  
  mutate(r.m = map(data, fun_dtm, "nest1", "nest2", "r")) %>% 
  mutate(samegroup.m = map(data, fun_dtm, "nest1", "nest2", "samegroup")) %>%
  setDT()
  

#[df_f_nested]----
df_f_nested <- combo_f %>%
  group_by(year, plot, colony) %>% 
  nest() %>% 
  mutate(dist.m = map(data, fun_dtm, "nest1", "nest2", "dist_m")) %>% 
  mutate(distz.m = map(data, fun_dtm, "nest1", "nest2", "dist_z")) %>%  
  mutate(r.m = map(data, fun_dtm, "nest1", "nest2", "r")) %>% 
  mutate(samegroup.m = map(data, fun_dtm, "nest1", "nest2", "samegroup")) %>%
  setDT()

saveRDS(df_m_nested, "../output/spatial_arrange/data/output_df_m_nested.rdata")
saveRDS(df_f_nested, "../output/spatial_arrange/data/output_df_f_nested.rdata")
```

#MRQAP test
```{r}
#create function: dist.m~r.m
f_mantel.r <- function(dist.m, r.m){
  asnipe::mrqap.dsp(dist.m ~ r.m,  intercept = T, directed = "undirected",
diagonal = F, test.statistic = "t-value", tol = 1e-07, randomisations = 1000)
}

# #dist~r+samegroup [zeros in samegroup.m and doesn't work]
# f_mantel.r2 <- function(dist.m, r.m, samegroup.m){
#   asnipe::mrqap.dsp(dist.m ~ r.m + samegroup.m,  intercept = T, directed = "undirected",
# diagonal = F, test.statistic = "t-value", tol = 1e-07, randomisations = 1000)
# }


#Run MRQAP
df_m_nested <- df_m_nested %>% 
  mutate(mantel.r = pmap(list(dist.m, r.m), f_mantel.r)) 

# df_f_nested <- df_f_nested %>% 
#   mutate(mantel.r = pmap(list(dist.m, r.m), f_mantel.r))  

#saveRDS(df_m_nested, "../output/spatial_arrange/data/output_mantel_dist and r_male.rdata")
#saveRDS(df_f_nested, "../output/spatial_arrange/data/output_mantel_dist and r_female.rdata")
```



#SKIP above and read the data set directly
#read output
```{r}
# df_m_nested <- readRDS("../output/spatial_arrange/data/output_mantel_dist and r_male.rdata") %>% setDT()
# df_f_nested <- readRDS("../output/spatial_arrange/data/output_mantel_dist and r_female.rdata") %>% setDT()

#add model results (estimates, pvalue)----
df_m_nested <- df_m_nested %>% 
  mutate(n_nests = map(dist.m, function(x)(dim(x)[[1]]))) %>% 
  mutate(coef.r = map(mantel.r, function(x)(x$"coefficients"[2]))) %>% 
  mutate(pvalue.r = map(mantel.r, function(x)(x$"P.values"[["r.m"]]))) 

df_f_nested <- df_f_nested %>% 
  mutate(n_nests = map(dist.m, function(x)(dim(x)[[1]]))) %>% 
  mutate(coef.r = map(mantel.r, function(x)(x$"coefficients"[2]))) %>% 
  mutate(pvalue.r = map(mantel.r, function(x)(x$"P.values"[["r.m"]]))) 

#unnest data
output_m.r <- df_m_nested %>% 
  select(year, plot, colony, n_nests, coef.r, pvalue.r) %>% 
  unnest(cols= c(n_nests, coef.r, pvalue.r))

# output_f.r <- df_f_nested %>% 
#   select(year, plot, colony, n_nests, coef.r, pvalue.r) %>% 
#   unnest(cols= c(n_nests, coef.r, pvalue.r))

# write_xlsx(output_m.r, paste0("../output/spatial_arrange/data/output_QAP_dist and r_male.xlsx"))
# write_xlsx(output_f.r, paste0("../output/spatial_arrange/data/output_QAP_dist and r_female.xlsx"))
```

#Meta-analysis
```{r}
library(metafor) # for metanalysis. 
library(igraph)
library(asnipe) # for lm on matrices
library(lme4)
library(car)
library(ggpubr) # for plotting correlations
library(Hmisc) # for multiple correlation 
library(car) # for collinearity
library(reshape2) # for melting matrices
library(lattice)
```

#import data
```{r}
df_m_nested <- readRDS("../output/spatial_arrange/data/output_mantel_dist and r_male.rdata") %>% setDT()
df_f_nested <- readRDS("../output/spatial_arrange/data/output_mantel_dist and r_female.rdata") %>% setDT()
```

##FUNCTION TO Get EFFECT SIZE
```{r}
# code for extracting r-squared and adjusted r-squared for the netlm 
# (adopted from Adriana)
adj.rsq <- function(x){
    
    mss <- sum((fitted(x) - mean(fitted(x)))^2)
    
    qn <- x$n
    df.int <- 1
    rdf <- qn - x$rank
    rss <- sum(resid(x)^2)
    #resvar <- rss/rdf
    
    r.squared <- mss/(mss + rss)
    adj.r.squared <- 1 - (1 - r.squared) * ((qn - df.int)/rdf)
    return(c(R2 = r.squared, adjR2 = adj.r.squared))
  }
  
  
# convert R2 to r (eq 13 in Nakagawa and Cuthill 2007)
  #If the R2 is a negative value it means that the model does not explain any of the variation.
  R2.to.r <- function(estimate, R2, N, k){ #input R2 from the model, k number of predictors in the model, n= sample size
    if (any(estimate >= 0)){
      r2 <- 1 - ( ((N-1) * (1-R2)) / (N-k-1) ) 
      r <- ifelse(r2 < 0, 0, (sqrt(r2)))
      return(r)
    } else {  # Make sure to carry the sign of the estimate
      r2 <- 1 - ( ((N-1) * (1-abs(R2))) / (N-k-1) )
      r <- ifelse(r2 < 0, 0, (-1 * (sqrt(r2))))
      return(r)
    }
  }
  
  
# Measures of effect size
  # For univariate analysis (eq 11 in Nakagawa and Cuthill 2007)
  t.to.r <-function(tval,df){
    r <- tval / (sqrt((tval^2) + df))
    return(r)
  }

```

#Effect size table
```{r}
m.m <- df_m_nested %>% 
  mutate(n_nests = map(dist.m, function(x)dim(x)[1])) %>% 
  select(year, plot, colony, n_nests, mantel.r) %>% 
  mutate(intercept = map(mantel.r, function(x)(x$coefficients[1])), 
         tval = map(mantel.r, function(x)(x$test.statistic[1])), 
         estimate = map(mantel.r, function(x)(x$coefficients[2])), #retrieve $r
         tval = map(mantel.r, function(x)(x$test.statistic[2])), 
         R2 = map(mantel.r, function(x)(adj.rsq(x)[[1]])),
         adj_R2 = map(mantel.r, function(x)(adj.rsq(x)[[2]])),
         df = map(mantel.r, function(x)(x$df.residual))) %>% 
  dplyr::select(-mantel.r) %>% 
  unnest(cols=c(n_nests, intercept, tval, estimate, tval, R2, adj_R2, df)) %>%
  mutate(se = estimate/tval) %>% 
  mutate(R2.r = R2.to.r(estimate, R2, N=n_nests, k=1)) %>% #"NAaNs" produced/it means r2<0 and R2.r is assigned as 0. It's fine. 
  mutate(t.r = t.to.r(tval, df)) %>%  #effect size
  left_join(select(tree_hei, year, colony, size_hei), by = c("year", "colony")) %>% 
  setDT()

```



#Meta-analysis
```{r}
# this one has lower AIC
model <-  rma.mv(yi=t.r, V=se, data=m.m,  method="REML", mods = ~ 1, random = list(~1|year, ~1|plot))

summary(model) # summary of the model
AIC(model) #108.57

#no effect on tree size
model2 <-  rma.mv(yi=t.r, V=se, data=m.m,  method="REML", mods = ~ size_hei, random = list(~1|year, ~1|plot))

summary(model2) # summary of the model
AIC(model2) #109.04

#
model3 <-  rma.mv(yi=t.r, V=se, data=m.m,  method="REML", mods = ~ 1, random = ~year|plot)

summary(model3) # summary of the model
AIC(model2) #109.04

# no random effect
model0 <-  rma(yi=t.r, sei=se, data=m.m,  method="REML", mods = ~ 1)

summary(model0)
AIC(model0) #112
```

#forest plot
```{r}
#ALL----
png(file = "../output/spatial_arrange/fig/Fig_r and dist_metanalysis_model_nz.png")
tiff(file = "../output/spatial_arrange/fig/Fig_r and dist_metanalysis_model_nz.tiff")

a <- forest.rma(model,
                header = c("Year Colony", "Effect size [95% CI]"),
                showweights = F,
                cex=0.6,
                at=c(-8, 0, 8),  
                slab=paste(m.m$year, m.m$colony), 
                xlim=c(-12,12),
                #ylim = c(-2, 43),
                order=order(m.m$t.r),
                col = "red")

#mtext(paste("Heterogeneity: ", expression(I^2), " = ", round(stab.model$I2, 2),sep=""), at = -0.35, line = -29.5, cex = 0.8)


dev.off()
```

#ggplot approach (make your forest plot pretty. Later)
```{r}
p=ggplot(dat, aes(y=year, x=yi, xmin=lowerci, xmax=upperci, shape = tester))+
  #Add data points and color them black
  geom_point(color = 'black')+
  #Add 'special' points for the summary estimates, by making them diamond shaped
  geom_point(data=subset(dat, tester=='Summary'), color='black', shape=18, size=4)+
  #add the CI error bars
  geom_errorbarh(height=.1)+
  #Specify the limits of the x-axis and relabel it to something more meaningful
  scale_x_continuous(limits=c(-2,2), name='Standardized Mean Difference (d)')+
  #Give y-axis a meaningful label
  ylab('Reference')+
  #Add a vertical dashed line indicating an effect size of zero, for reference
  geom_vline(xintercept=0, color='black', linetype='dashed')+
  #Create sub-plots (i.e., facets) based on levels of setting
  #And allow them to have their own unique axes (so authors don't redundantly repeat)
  facet_grid(setting~., scales= 'free', space='free')+
  #Apply my APA theme
  apatheme
p
```


#calculate I^2
```{r}
#this part looks strange, very low I^2
W <- diag(1/m.m$se)
X <- model.matrix(model)
P <- W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
100 * sum(model$sigma2) / (sum(model$sigma2) + (model$k-model$p)/sum(diag(P)))
```
#********END of META-ANALYSIS************#



#*************Order of relatives**********#
#TIDY DATA
```{r}
#[unicombo_m]----
unicombo_m <- m %>% 
  group_by(year, plot, colony) %>% 
  group_modify(., ~ as.data.frame.matrix(t(combn(.$nest, 2)), stringsAsFactors = F)) %>%
  rename("nest1" = "V1", "nest2" = "V2") %>% 
  left_join(m, by=c("year","plot","colony","nest1"="nest")) %>% 
  left_join(m, by=c("year","plot","colony","nest2"="nest"), suffix=c("1", "2")) %>%
  as.data.table() %>% 
  mutate(dist_m = fun_weight(.[,.(nest1, nest2)], nestdist, "dist_m"), 
         dist_z = fun_weight(.[,.(nest1, nest2)], nestdist, "dist_z"), 
         r = fun_weight(.[,.(m1, m2)],relate, "r"), 
         kinship = fun_kinship(.[,.(m1, m2)], kinship, "kinorder"), 
         #kinship2 = fun_kinship(.[,.(m1, m2)], kinship, "kinorder2"), 
         sex12="MM") %>% 
  #mutate(kinship = ordered(kinship, levels = c("first", "second", "DR", "UR"))) %>%
  mutate(r = replace_na(r, 1)) %>% 
  left_join(mygroup_ssa[gtype=="daytime",.(year, plot, id, groupid)], by=c("year", "plot", "m1"="id")) %>% 
  left_join(mygroup_ssa[gtype=="daytime",.(year, plot, id, groupid)], by=c("year", "plot", "m2"="id"), suffix-c("_1","_2")) %>% 
  mutate(samegroup = as.factor(ifelse(groupid.x == groupid.y, 1, 0))) %>% 
  mutate(samegroup = ordered(samegroup, levels=c("1","0"))) %>% 
  setDT()

unicombo_f <- f %>% 
  group_by(year, plot, colony) %>% 
  group_modify(., ~ as.data.frame.matrix(t(combn(.$nest, 2)), stringsAsFactors = F)) %>%
  rename("nest1" = "V1", "nest2" = "V2") %>% 
  left_join(f, by=c("year","plot","colony","nest1"="nest")) %>% 
  left_join(f, by=c("year","plot","colony","nest2"="nest"), suffix=c("1", "2")) %>%
  as.data.table() %>% 
  mutate(dist_m = fun_weight(.[,.(nest1, nest2)], nestdist, "dist_m"), 
         dist_z = fun_weight(.[,.(nest1, nest2)], nestdist, "dist_z"), 
         r = fun_weight(.[,.(f1, f2)],relate, "r"), 
         kinship = fun_kinship(.[,.(f1, f2)], kinship, "kinorder"), 
         #kinship2 = fun_kinship(.[,.(f1, f2)], kinship, "kinorder2"), 
         sex12="FF") %>% 
  #mutate(kinship = ordered(kinship, levels = c("first", "second", "DR", "UR"))) %>%
  mutate(r = replace_na(r, 1)) %>% 
  left_join(mygroup_ssa[gtype=="daytime",.(year, plot, id, groupid)], by=c("year", "plot", "f1"="id")) %>% 
  left_join(mygroup_ssa[gtype=="daytime",.(year, plot, id, groupid)], by=c("year", "plot", "f2"="id"), suffix-c("_1","_2")) %>% 
  mutate(samegroup = as.factor(ifelse(groupid.x == groupid.y, 1, 0))) %>% 
  mutate(samegroup = ordered(samegroup, levels=c("1","0"))) %>% 
  setDT()

#all
unicombo_mf <- rbind(unicombo_m, unicombo_f, use.names=F) %>% rename(id1=m1,id2=m2)
```

#summary stats of nest dist and order of relatives
```{r}
sum_m <- unicombo_m %>% 
  group_by(kinship) %>% 
  summarise(mean_dist = mean(dist_m), sd = sd(dist_m))

sum_f <- unicombo_f %>% 
  group_by(kinship) %>% 
  summarise(mean_dist = mean(dist_m), sd = sd(dist_m))
```


#GGBOXPLOT
```{r}
ggboxplot(unicombo_mf, x="kinship", y="dist_m", fill="sex12", palette = "jco", ylab = "Nest distance (m)", xlab="Kinship")
ggviolin(unicombo_mf, x="kinship", y="dist_m", fill="sex12", palette = "jco", ylab = "Nest distance (m)", xlab="Kinship")

ggscatter(unicombo_mf, x="r", y="dist_m", color="sex12", add = "reg.line")
```

#Male
```{r}
#ggboxplot(unicombo_m, x="kinship", y="dist_m", fill="samegroup", palette = "jco", ylab = "Nest distance (m)", xlab="Kinship", add= "jitter") +
ggviolin(unicombo_m, x="kinship", y="dist_m", fill="samegroup", palette = "jco", ylab = "Nest distance (m)", xlab="Kinship") +
  
theme(#axis.text.x = element_text(size=7),
        axis.text.y = element_text(face="bold", size=10),
        axis.title.x = element_text(face="bold", size=14),
        axis.title.y = element_text(face="bold", size=14)) +
  scale_x_discrete(labels=c("first" = "First-order", "second" = "Second-order", "UR"="Unrelated"))
  
ggsave("../output/spatial_arrange/fig/fig_boxplot_dist and r and samegroup.png")

#
ggboxplot(unicombo_m, x="kinship", y="dist_m", ylab = "Nest distance (m)", xlab="Kinship", fill = "grey50") + 
  theme(#axis.text.x = element_text(size=7),
        axis.text.y = element_text(face="bold", size=10),
        axis.title.x = element_text(face="bold", size=14),
        axis.title.y = element_text(face="bold", size=14)) +
  scale_x_discrete(labels=c("first" = "First-order", "second" = "Second-order", "UR"="Unrelated"))
  
ggsave("../output/spatial_arrange/fig/fig_boxplot_dist and r.png")

```

#Female
```{r}
ggboxplot(unicombo_f, x="kinship", y="dist_m", fill="samegroup", palette = "jco", ylab = "Nest distance (m)", xlab="Kinship") +

theme(#axis.text.x = element_text(size=7),
        axis.text.y = element_text(face="bold", size=10),
        axis.title.x = element_text(face="bold", size=14),
        axis.title.y = element_text(face="bold", size=14)) +
  scale_x_discrete(labels=c("first" = "First-order", "second" = "Second-order", "UR"="Unrelated"))
  


#
ggboxplot(unicombo_f, x="kinship", y="dist_m", ylab = "Nest distance (m)", xlab="Kinship", fill = "grey50") + 
  theme(#axis.text.x = element_text(size=7),
        axis.text.y = element_text(face="bold", size=10),
        axis.title.x = element_text(face="bold", size=14),
        axis.title.y = element_text(face="bold", size=14)) +
  scale_x_discrete(labels=c("first" = "First-order", "second" = "Second-order", "UR"="Unrelated"))
  
```

#------OWNED nests and social levels------
#PAIR nest
```{r}
#"Paired males normally maintained one nest (1.10 ± 0.25, n = 128) while some pairs (10 %) may owned two nests."
#[nest_pair]----
nest_pair <- sum_sleepnest %>% 
  filter(n_nights>=3 & order_sex == 1) %>% 
  group_by(year, colony, nest) %>% #$color
  select(year, plot, colony, nest, color, sex) %>% 
  pivot_wider(., names_from = "sex", values_from = "color") %>% 
  as.data.table() %>% 
  mutate(dyadID = fun_kinship(.[,.(m,f)], dyadID, "dyadID")) %>% 
  filter(!is.na(dyadID)) %>%  #only pairs
  setDT()

#summary of how many nests do males have?
#only 12% male maintained more than one nest within a season
sum_m_nest <- nest_pair %>% 
  filter(!is.na(dyadID)) %>% 
  group_by(m, year, plot, colony) %>% 
  summarise(n_nest = n()) 

sum_m_nest_colonymean <- sum_m_nest %>% 
  group_by(m, year, plot) %>%
  summarise(n_nest = mean(n_nest))

sum_m_nest_yearmean <- sum_m_nest_colonymean %>% 
  group_by(m) %>%
  summarise(n_nest = mean(n_nest))

sum2_m_nest_yearmean <- sum_m_nest_yearmean %>% 
  ungroup() %>% 
  summarise(mean = mean(n_nest), sd = sd(n_nest), median = median(n_nest))

view(sum_m_nest)
view(sum_m_nest_colonymean)
view(sum_m_nest_yearmean)
view(sum2_m_nest_yearmean)
```

## number of nests by GROUP/unit type
```{r}
#[nest_group]----
#IMPORTANT FILE----
nest_group <- sum_sleepnest %>% 
  filter(n_nights>=3 & order_sex == 1) %>%
  select(year, plot, colony, nest, color, sex) %>% 
  left_join(mygroup_ssa[gtype=="daytime", .(year, plot, id, groupid)], by = c("year","plot","color"="id")) %>% 
  select(year, plot, colony, nest, groupid) %>% 
  distinct() %>% 
  left_join(Dgroup_unit, by=c("groupid", "year", "plot")) %>% 
  filter(!is.na(groupid)) %>%  #n=3 nests, those inds were not belonged to any daytime group

view(nest_group)

#[sum_nest_group]----
#how many nests does a daytime group has?
sum_nest_group <- nest_group %>% 
  group_by(year, plot, colony, groupid, unit) %>% 
  summarise(n_nest = n()) 

view(sum_nest_group)

#[sum_nest_unit]----
#sum by famliy type
sum_nest_unit <- sum_nest_group %>%
  group_by(year, plot, unit, groupid) %>% 
  summarise(n_nest = mean(n_nest)) %>% 
  group_by(unit) %>% 
  summarise(mean = mean(n_nest), sd = sd(n_nest), median = median(n_nest), min = min(n_nest), max = max(n_nest)) 

   #NA unit is produced by 14MDg11(gs=1) and was not included in unit analysis
   #group size =1; 14MDg11, 15LDg27, 17LDg30
view(sum_nest_unit)

#[sum_nest_unit_pro]----
#sum by famliy type
sum_nest_unit_pro <- sum_nest_group %>%
  group_by(unit, n_nest) %>%
  summarise(n= n()) %>% 
  group_by(unit) %>% 
  mutate(pro = n/sum(n)) %>% 
  arrange(-pro, .by_group=T)

   #NA unit is produced by 14MDg11(gs=1) and was not included in unit analysis
   #group size =1; 14MDg11, 15LDg27, 17LDg30
view(sum_nest_unit)
view(sum_nest_unit_pro)


write_xlsx(sum_nest_unit, "../output/spatial_arrange/data/output_sum_nest_unit.xlsx")  
```



