#title: "Chap1 analysis r and association"

```{r}
library(dplyr)
```


## convert assocation matrix to dataframe
## Tidy your data
##this includes all combo for the plot, only from systematic sampling
```{r}
#convert matrix to dataframe
f_mtod <- function(x){
  d <- x %>% 
  modify_if(., upper.tri(., diag = F), ~ NA) %>%  #include diagonal (F)
    reshape2::melt(., na.rm = T) %>% 
    rename(id1 = Var1, id2 = Var2, association = value) %>%
    mutate(id1 = as.character(id1), id2 = as.character(id2)) 
  return(d)
}
```

```{r}
df_D <- lapply(Dadjm.pssa, f_mtod) %>% rbindlist(., idcol = "list") %>% mutate(gtype="daytime")
df_N <- lapply(Nadjm.pssa, f_mtod) %>% rbindlist(., idcol = "list") %>% mutate(gtype="sleeping")
df_B <- lapply(Badjm.p, f_mtod) %>% rbindlist(., idcol = "list") %>% mutate(gtype="breeding")

```

#tidy data
```{r}
#[df0]----
#contain diagonal
#this contains assocations year X plot X gtype
df0 <- rbind(df_D, df_N, df_B) %>%  
  filter(id1 != "MYPO" & id2 != "MYPO") %>% #delete ind with no genetic data, n=131497
  mutate(id12 = paste0(id1, id2)) %>% 
  mutate(year = paste0("20", substr(list, 6, 7)), 
         plot = if_else(str_detect(list, "M"), "MSTO", 
                  if_else(str_detect(list, "L"), "LLOD", "SPRA"))) %>% 
  select(-list) %>% 
  mutate(V1sex = fun_sexdyad(., sex)[[1]], 
           V2sex = fun_sexdyad(., sex)[[2]],
           V12sex = fun_sexdyad(., sex)[[3]]) %>% 
  mutate(mat1.m = ifelse(V12sex=="mm", 1, 0)) %>% #mm:10, ff:01, mf:00
  mutate(mat2.f = ifelse(V12sex=="ff", 1, 0)) %>% 
  mutate(r = fun_r(., relate[, r:= wang])) %>% #add $r
  mutate(r = ifelse(id1==id2, 1, r)) %>% 
  mutate(kin_final = fun_kinship(., kinship, "kin_final"),  #get $kinship 
         kin_kg = fun_kinship(., kinship, "kin_kg"), 
         kin_kg2 = fun_kinship(., kinship, "kin_kg2"),
         kinorder = fun_kinship(., kinship, "kinorder"), 
         kinorder2 = fun_kinship(., kinship, "kinorder2"),
         UR = fun_kinship(., kinship, "UR12")) %>% 
  left_join(select(pair, year, plot, V1, V2, pair), by=c("year", "plot","id1"="V1", "id2"="V2")) %>%   #add pair, one id could have two pairs!
  mutate(pair = replace(pair, is.na(pair), 0)) %>% 
  left_join(select(colony_member_main1, year, plot,  color, colony), 
            by = c("year", "plot", "id1" = "color")) %>% 
  rename(id1_colony = colony ) %>% 
  left_join(select(colony_member_main1, year, plot, color, colony), 
            by = c("year", "plot", "id2" = "color")) %>% 
  rename(id2_colony = colony) %>% 
  mutate(samecolony = ifelse(id1_colony == id2_colony, 1, 0)) %>% 
  mutate(samecolony = replace_na(samecolony, 0))  #assume not in the same colony if no colony membership for the bird

```


#some function
```{r}
#convert data to $AI.m
faso <-  function(data){
 x <- data %>% 
    dplyr::select(id1, id2, association) %>% 
    spread(key = id2, value = association, fill = 0) %>% 
    column_to_rownames(., var = "id1") %>% 
    as.matrix()
 x2 <- x + t(x)
 return(x2)
}


#convert data to $r.m
fr <- function(data){
  x <- data %>% 
    dplyr::select(id1, id2, r) %>% 
    spread(key = id2, value = r, fill = 0) %>% 
    column_to_rownames(., var = "id1") %>% 
    as.matrix()
  x2 <- x + t(x)
  diag(x2) <- 1
  return(x2)
}

#convert data to $sex1.m, $sex2.m
#mm:10, mf:11, ff:01
fsex1 <- function(data){
  x <- data %>% 
    dplyr::select(id1, id2, mat1.m) %>% 
    spread(key = id2, value = mat1.m, fill = 0) %>% 
    column_to_rownames(., var = "id1") %>% 
    as.matrix()
  x2 <- x + t(x)
  diag(x2) <- 1
  return(x2)
}

fsex2 <- function(data){
  x <- data %>% 
    dplyr::select(id1, id2, mat2.f) %>% 
    spread(key = id2, value = mat2.f, fill = 0) %>% 
    column_to_rownames(., var = "id1") %>% 
    as.matrix()
  x2 <- x + t(x)
  diag(x2) <- 1
  return(x2)
}

#convert data to $pair.m
fpair <- function(data){
  x <- data %>% 
    dplyr::select(id1, id2, pair) %>% 
    spread(key = id2, value = pair, fill = 0) %>% 
    column_to_rownames(., var = "id1") %>% 
    as.matrix()
  x2 <- x + t(x)
  diag(x2) <- 1
  return(x2)
}

#convert data to $colony.m
fcolony <- function(data){
  x <- data %>% 
    dplyr::select(id1, id2, samecolony) %>% 
    spread(key = id2, value = samecolony, fill = 0) %>% 
    column_to_rownames(., var = "id1") %>% 
    as.matrix()
  x2 <- x + t(x)
  diag(x2) <- 1
  return(x2)
}
```

##Into nested data mode
```{r}
#[df_nested]----
df_nested <- df0 %>%
  group_by(year, plot, gtype) %>% 
  nest() %>% 
  mutate(AI.m = map(data, faso), #add $AI.m, $data is a list-column now
         r.m = map(data, fr), 
         sexm.m = map(data, fsex1),
         sexf.m = map(data, fsex2),
         pair.m = map(data, fpair),
         colony.m = map(data, fcolony))  #add $r.m

#check matrix before running test
isSymmetric(df_nested$AI.m[[1]])

#saveRDS(df_nested, "../output/r and association/data/df_nested_SS_all.rdata")
```
ˇˇ
#MRQAP test
```{r}
#create function
f_mantel.r3 <- function(AI.m, r.m, pair.m, colony.m){
  asnipe::mrqap.dsp(AI.m ~ r.m + pair.m + colony.m,  intercept = T, directed = "undirected",
diagonal = F, test.statistic = "t-value", tol = 1e-07, randomisations = 1000)
}

#Run MRQAP (took a long time)
df_nested3 <- df_nested %>% 
  mutate(mantel.r3 = pmap(list(AI.m, r.m, pair.m, colony.m), f_mantel.r3)) #run parallel map on list-columns

#saveRDS(df_nested3, "../output/r and association/data/output_mantel_r3.rdata")
```

#SKIP above and read the data set directly
#read output
```{r}
df_nested3 <- readRDS("../output/r and association/data/output_mantel_r3.rdata") %>% setDT()

#add model results (estimates, pvalue)----
df_nested3 <- df_nested3 %>% 
  mutate(n_birds = map(AI.m, function(x)(dim(x)[[1]]))) %>% 
  mutate(coef.r3 = map(mantel.r3, function(x)(x$"coefficients"[2]))) %>% 
  mutate(pvalue.r3 = map(mantel.r3, function(x)(x$"P.values"[["r.m"]]))) %>% 
  mutate(coef.pair.r3 = map(mantel.r3, function(x)(x$"coefficients"[3]))) %>% 
  mutate(pvalue.pair.r3 = map(mantel.r3, function(x)(x$"P.values"[["pair.m"]]))) %>% 
  mutate(coef.colony.r3 = map(mantel.r3, function(x)(x$"coefficients"[4]))) %>% 
  mutate(pvalue.colony.r3 = map(mantel.r3, function(x)(x$"P.values"[["colony.m"]]))) 


#unnest data
output.r3 <- df_nested3 %>% 
  select(year, plot, gtype, n_birds, coef.r3, pvalue.r3, coef.pair.r3, pvalue.pair.r3, coef.colony.r3, pvalue.colony.r3) %>% 
  unnest(cols= c(n_birds, coef.r3, pvalue.r3, coef.pair.r3, pvalue.pair.r3, coef.colony.r3, pvalue.colony.r3))

#saveRDS(df_nested3, paste0("../output/r and association/data/df_nested_AI and r3_SS_all.rdata"))
#write_xlsx(output.r3, paste0("../output/r and association/data/output_QAP_AI and r3_SS_all.xlsx"))
```

#Meta-analysis
```{r}
library(metafor) # for metanalysis. 
library(igraph)
library(asnipe) # for lm on matrices
library(lme4)
library(car)
library(ggpubr) # for plotting correlations
library(Hmisc) # for multiple correlation 
library(car) # for collinearity
library(reshape2) # for melting matrices
library(lattice)
```

#import data
```{r}
df_nested3 <- readRDS("../output/r and association/data/df_nested_AI and r3_SS_all.rdata")
```



##FUNCTION TO Get EFFECT SIZE
```{r}
# code for extracting r-squared and adjusted r-squared for the netlm 
# (adopted from Adriana)
adj.rsq <- function(x){
    
    mss <- sum((fitted(x) - mean(fitted(x)))^2)
    
    qn <- x$n
    df.int <- 1
    rdf <- qn - x$rank
    rss <- sum(resid(x)^2)
    resvar <- rss/rdf
    
    r.squared <- mss/(mss + rss)
    adj.r.squared <- 1 - (1 - r.squared) * ((qn - df.int)/rdf)
    return(c(R2 = r.squared, adjR2 = adj.r.squared))
  }
  
  
# convert R2 to r (eq 13 in Nakagawa and Cuthill 2007)
  #If the R2 is a negative value it means that the model does not explain any of the variation.
  R2.to.r <- function(estimate, R2, N, k){ #input R2 from the model, k number of predictors in the model, n= sample size
    if (any(estimate >= 0)){
      r2 <- 1 - ( ((N-1) * (1-R2)) / (N-k-1) ) 
      r <- ifelse(r2 < 0, 0, (sqrt(r2)))
      return(r)
    } else {  # Make sure to carry the sign of the estimate
      r2 <- 1 - ( ((N-1) * (1-abs(R2))) / (N-k-1) )
      r <- ifelse(r2 < 0, 0, (-1 * (sqrt(r2))))
      return(r)
    }
  }
  
  
# Measures of effect size
  # For univariate analysis (eq 11 in Nakagawa and Cuthill 2007)
  t.to.r <-function(tval,df){
    r <- tval / (sqrt((tval^2) + df))
    return(r)
  }

```

#Effect size table
```{r}
m <- df_nested3 %>% 
  select(year, plot, gtype, n_birds, mantel.r3) %>% 
  mutate(intercept = map(mantel.r3, function(x)(x$coefficients[1])), 
         tval = map(mantel.r3, function(x)(x$test.statistic[1])), 
         estimate = map(mantel.r3, function(x)(x$coefficients[2])), #retrieve $r
         tval = map(mantel.r3, function(x)(x$test.statistic[2])), 
         R2 = map(mantel.r3, function(x)(adj.rsq(x)[[1]])),
         adj_R2 = map(mantel.r3, function(x)(adj.rsq(x)[[2]])),
         df = map(mantel.r3, function(x)(x$df.residual))) %>% 
  unnest(cols=c(n_birds, intercept, tval, estimate, tval, R2, adj_R2, df)) %>%
  dplyr::select(-mantel.r3) %>% 
  mutate(se = estimate/tval) %>% 
  mutate(R2.r = R2.to.r(estimate, R2, N=n_birds, k=3), 
         t.r = t.to.r(tval, df)) %>%  #effect size
  mutate(label = paste(year, plot, gtype, sep="."), 
         yearplot = paste(year, plot)) %>% 
  filter(!is.na(t.r)) %>% 
  mutate(gtype = ordered(gtype, levels = c("daytime", "sleeping", "breeding")), 
         plot = ordered(plot, levels = c("MSTO", "SPRA", "LLOD"))) %>% 
  arrange(gtype, year, plot) %>% 
  setDT()

#time
m.D <- m %>% filter(gtype=="daytime")
m.N <- m %>% filter(gtype=="sleeping")
m.B <- m %>% filter(gtype=="breeding")
```



#Meta-analysis
```{r}
# Meta-analysis (need $t.r, $se)
model <-  rma.mv(yi=t.r, V=se, data=m,  method="REML", mods = ~ 1, random = list(~1|gtype, ~1|year, ~1|plot))

summary(model) # summary of the model

#sepearate gtype
model.D <-  rma.mv(yi=t.r, V=se, data=m.D,  method="REML", mods = ~ 1, random = list(~1|year, ~1|plot))

summary(model.D) # summary of the model

#
model.N <-  rma.mv(yi=t.r, V=se, data=m.N,  method="REML", mods = ~ 1, random = list(~1|year, ~1|plot))

summary(model.N) # summary of the model

#
model.B <-  rma.mv(yi=t.r, V=se, data=m.B,  method="REML", mods = ~ 1, random = list(~1|year, ~1|plot))

summary(model.B) # summary of the model
```

#forest plot
```{r}
#ALL----
png(file = "../output/r and association_metanalysis/fig/Fig_r and aso_metanalysis_model3_SS_all.png") 

a <- forest.rma(model,
                header = c("Year Site", "Effect size [95% CI]"),
                cex=0.8,
                at=c(-1, -0.5, 0, 0.5, 1),  
                slab=paste(m$year, m$plot, m$gtype, sep=", "), 
                ylim = c(-2, 43),
                #rows=c(41:29, 27:15, 13:1), #this separates rows
                #order=order(m$t.r),
                col = "red")

dev.off()

#Daytime ----
png(file = "../output/r and association_metanalysis/fig/Fig_Daytime_r and aso_metanalysis_model3_SS_all.png") 

a <- forest.rma(model.D,
                order = order(m.D$t.r),
                header = c("Year Site", "Effect size [95% CI]"),
                cex=0.8,
                xlim = c(-1,1.5),
                at=c(-0.5, 0, 0.5, 0.8),
                slab=paste(m.D$year, m.D$plot, sep=","),
                col = "red"
                      )
text(c(.1),  16.5, c("Daytime"), font=2)


dev.off()

#sleeping ----
png(file = "../output/r and association_metanalysis/fig/Fig_Nighttime_r and aso_metanalysis_model3_SS_all.png", width = 480, height = 480) 

a <- forest(model.N,
            order = order(m.N$t.r),
            header = c("Year Site", "Effect size [95% CI]"),
            cex=0.8,
            xlim = c(-1,1.5),
            at=c(-0.5, 0, 0.5, 0.8),
            slab=paste(m.N$year, m.N$plot, sep="."),
            col = "red")
text(c(.1),  16.5, c("Nighttime"), font=2)

dev.off()

#breeding ----
png(file = "../output/r and association_metanalysis/fig/Fig_breeding_r and aso_metanalysis_model3.png") 

a <- forest.rma(model.B,
                order = order(m.B$t.r),
                header = c("Year Site", "Effect size [95% CI]"),
                cex=0.8,
                xlim = c(-1,1.5),
                at=c(-0.5, 0, 0.5, 0.8),
                slab=paste(m.B$year, m.B$plot),
                col = "red")
text(c(.1),  16.5, c("Breeding"), font=2)
dev.off()
```
#************END of MODEL************#






#*************************************************************#
#-----MODEL: AI~r + pair----
```{r}
#create function
f_mantel.r2 <- function(AI.m, r.m, pair.m){
  asnipe::mrqap.dsp(AI.m ~ r.m + pair.m,  intercept = T, directed = "undirected",
diagonal = F, test.statistic = "t-value", tol = 1e-07, randomisations = 1000)
}

#Run MRQAP (took a long time)
df_nested2 <- df_nested %>% 
  mutate(mantel.r2 = pmap(list(AI.m, r.m, pair.m), f_mantel.r2)) #run parallel map on list-columns

#saveRDS(df_nested2, "../output/r and association/data/output_mantel_r2.rdata")
```

#SKIP above and read the data set directly
#read output
```{r}
df_nested2 <- readRDS("../output/r and association/data/output_mantel_r2.rdata") %>% setDT()

#add model results (estimates, pvalue)----
df_nested2 <- df_nested2 %>% 
  mutate(n_birds = map(AI.m, function(x)(dim(x)[[1]]))) %>% 
  mutate(coef.r2 = map(mantel.r2, function(x)(x$"coefficients"[2]))) %>% 
  mutate(pvalue.r2 = map(mantel.r2, function(x)(x$"P.values"[["r.m"]]))) %>% 
  mutate(coef.pair.r2 = map(mantel.r2, function(x)(x$"coefficients"[3]))) %>% 
  mutate(pvalue.pair.r2 = map(mantel.r2, function(x)(x$"P.values"[["pair.m"]]))) 


#unnest data
output.r2 <- df_nested2 %>% 
  select(year, plot, gtype, n_birds, coef.r2, pvalue.r2, coef.pair.r2, pvalue.pair.r2) %>% 
  unnest(cols= c(n_birds, coef.r2, pvalue.r2, coef.pair.r2, pvalue.pair.r2))

#saveRDS(df_nested2, paste0("../output/r and association/data/df_nested_AI and r2_SS_all.rdata"))
#write_xlsx(output.r2, paste0("../output/r and association/data/output_QAP_AI and r2_SS_all.xlsx"))
```

#Meta-analysis: model 2 (AI~r+pair)
#Effect size table
```{r}
#not sure why 2015M, sleeping is NA???
m2 <- df_nested2 %>% 
  select(year, plot, gtype, n_birds, mantel.r2) %>% 
  mutate(intercept = map(mantel.r2, function(x)(x$coefficients[1])), 
         tval = map(mantel.r2, function(x)(x$test.statistic[1])), 
         estimate = map(mantel.r2, function(x)(x$coefficients[2])), #retrieve $r
         tval = map(mantel.r2, function(x)(x$test.statistic[2])), 
         R2 = map(mantel.r2, function(x)(adj.rsq(x)[[1]])),
         adj_R2 = map(mantel.r2, function(x)(adj.rsq(x)[[2]])),
         df = map(mantel.r2, function(x)(x$df.residual))) %>% 
  unnest(cols=c(n_birds, intercept, tval, estimate, tval, R2, adj_R2, df)) %>%
  dplyr::select(-mantel.r2) %>% 
  mutate(se = estimate/tval) %>% 
  mutate(R2.r = R2.to.r(estimate, R2, N=n_birds, k=3), 
         t.r = t.to.r(tval, df)) %>%  #effect size
  mutate(label = paste(year, plot, gtype, sep="."), 
         yearplot = paste(year, plot)) %>% 
  filter(!is.na(t.r)) %>% 
  mutate(gtype = ordered(gtype, levels = c("daytime", "sleeping", "breeding")), 
         plot = ordered(plot, levels = c("MSTO", "SPRA", "LLOD"))) %>% 
  arrange(gtype, year, plot) %>% 
  setDT()

#time
m2.D <- m2 %>% filter(gtype=="daytime")
m2.N <- m2 %>% filter(gtype=="sleeping")
m2.B <- m2 %>% filter(gtype=="breeding")
```


```{r}
# Meta-analysis (need $t.r, $se)
model2 <-  rma.mv(yi=t.r, V=se, data=m2,  method="REML", mods = ~ 1, random = list(~1|gtype, ~1|year, ~1|plot))

summary(model2) # summary of the model

#sepearate gtype
model2.D <-  rma.mv(yi=t.r, V=se, data=m2.D,  method="REML", mods = ~ 1, random = list(~1|year, ~1|plot))

summary(model2.D) # summary of the model

#
model2.N <-  rma.mv(yi=t.r, V=se, data=m2.N,  method="REML", mods = ~ 1, random = list(~1|year, ~1|plot))

summary(model2.N) # summary of the model

#
model2.B <-  rma.mv(yi=t.r, V=se, data=m2.B,  method="REML", mods = ~ 1, random = list(~1|year, ~1|plot))

summary(model2.B) # summary of the model
```

#forest plot: MODEL2(AI~r + pair)
```{r}
#ALL----
png(file = "../output/r and association_metanalysis/fig/Fig_r and aso_metanalysis_model2_SS_all.png") 

forest.rma(model2,
                      header = c("Year Site", "Effect size [95% CI]"),
                     cex=0.8,
                      at=c(-1, -0.5, 0, 0.5, 1),
                      slab=paste(m$year, m$plot, m$gtype, sep=", "), 
                      col = "red")

dev.off()

#Daytime ----
png(file = "../output/r and association_metanalysis/fig/Fig_Daytime_r and aso_metanalysis_model2_SS_all.png") 

forest.rma(model2.D,
                      header = c("Year Site", "Effect size [95% CI]"),
                      cex=0.8,
                      at=c(-1, -0.5, 0, 0.5, 1),
                      slab=paste(m.D$year, m.D$plot, sep=","),
                      col = "red", 
                      )

dev.off()

#sleeping ----
png(file = "../output/r and association_metanalysis/fig/Fig_Nighttime_r and aso_metanalysis_model2_SS_all.png") 

a <- forest(model2.N,
            header = c("Year Site", "Effect size [95% CI]"),
            order=order(m.N$t.r),
                     cex=0.8,
                     at=c(-1, -0.5, 0, 0.5, 1),
                     slab=paste(m.N$year, m.N$plot, sep="."),
                     col = "red")

dev.off()

#breeding ----
png(file = "../output/r and association_metanalysis/fig/Fig_breeding_r and aso_metanalysis_model2.png") 

forest.rma(model2.B,
                     header = c("Year Site", "Effect size [95% CI]"),
                     cex=0.8,
                      at=c(-1, -0.5, 0, 0.5, 1),
                      slab=paste(m.B$year, m.B$plot),
                      col = "red")

dev.off()
```


