---
title: "GCSW_chap1_finding groups"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#Gaussian mixed model
```{r}
#this can run for a long time for a big data set
fun_gmm <- function(daytime, breeding = c("B", "BNB"), cutoff){
  point_data_all <- daytime %>% 
    filter(sec > 0) %>% #exclude data outside sampling range
    left_join(BD[,.(nest_date, nestid)], by="nest_date") %>% #add $nestid, $stage
    left_join(sum_bird_nest_BNB, by = c("year", "color", "nest"))
  
  if(breeding == "B"){
    point_data_all <- point_data_all %>%  
      filter(!is.na(nestid)) %>% #filter breeding stage
      filter(BNB_visit > cutoff & B_visit > cutoff)  #filter cutoff
  }
  if(breeding == "BNB"){
    point_data_all <- point_data_all %>% 
      filter(BNB_visit > cutoff) #filter cutoff
  }
  if(breeding == "NB"){
    point_data_all <- point_data_all %>%  
      filter(is.na(nestid)) %>% #filter breeding stage
      filter(BNB_visit > cutoff)  #filter cutoff
  }
  
  point_data_all <- point_data_all %>% 
    select(date, timestamp.1m, color, nest, nestdate_sec) %>%   #$nest_date as $location
    mutate(date = yday(date)) %>%  #convert to julian day
    mutate(timestamp.1m = as.numeric(timestamp.1m)) %>% setDT()
  
  sec_l2 <- point_data_all %>% count(nestdate_sec) %>% filter(n > 2)
  
  point_data <- point_data_all %>% filter(nestdate_sec %in% sec_l2$nestdate_sec)
  
  global_ids <- levels(point_data$color)
  
  gmm_data <- asnipe::gmmevents(time = point_data$timestamp.1m,
                                identity = point_data$color,
                                location = point_data$nestdate_sec,
                                global_ids=global_ids
  )
  #group name to add in the filename
  groupname <- paste0(substr(unique(daytime$year), 3, 4), substr(unique(daytime$plot), 1, 1))
  
  #output your gmm data!!
  saveRDS(gmm_data, file = paste0("../output/data/gmm/", breeding, "/v", cutoff, "/", paste0("gmm_", breeding, "_", groupname, "_v", cutoff, ".RData")))
  
}
#------end of function----#
```

#Generate gbi data (this runs a long time)
```{r}
cutoff = 1  
breeding = "BNB" #B: breeding; BNB:breeding and non-breeding; NB: non-breeding

#output gmm data by year, plot
daytime.list <- daytime %>% split(list(.$year, .$plot), drop = T)

lapply(daytime.list, fun_gmm, breeding, cutoff)
```

#--------DAYTIME---------#
#Generate adjacency matrix and network objects
```{r}
cutoff = 1
group_type = "BNB"  #B, NB, BNB
index = "SRI"
format = "gbi"

data_type = "gmm"
g_type = "daytime" #breeding or daytime
g_type2 = "B" #breeding = "B", daytime = "D"
```

```{r}
#import gmm files, 
b <- list.files(paste0("../output/data/gmm/", group_type, "/v", cutoff))

#generate list with gbi and event
f <- function(b){
  a <- readRDS(paste0("../output/data/gmm/", group_type, "/v", cutoff, "/", b))
  
  event <- a$metadata %>% 
    mutate(date = str_split_fixed(Location, "_", n=3)[,2], 
         nest = str_split_fixed(Location, "_", n=3)[,1]) %>% 
    mutate(date = lubridate::mdy(date), 
           year = as.character(year(date))) %>%
    mutate(duration_min = (End - Start)/60) %>% #sampling intervals 
    left_join(nest_list_uni, by = c("nest")) %>%  #add $colony
    left_join(select(colonywise_sampledate, colony, date, colony_sampled_D), by = c("colony","date")) %>% 
    left_join(select(colony_excluded, year, colony, excluded), by = c("year", "colony")) %>%
    mutate(excluded = replace_na(excluded, 0)) %>%
    setDT()
  
  #only systematic sampling and <2hrs sampling interval
  position_ss <- which(event$colony_sampled_D==1 & event$duration_min <=120)
  
  event_select <- event[position_ss,]
  gbi <- a$gbi[position_ss, ]
  nzindex <- which(colSums(gbi)>0)
  gbi <- gbi[,nzindex]
  
  outputlist <- list("gbi" = gbi, "event" = event_select)
  return(outputlist)
}

# make a list for gmm data from all plots, years
gmm.list <- lapply(b, f)  

# add name to the list
#names(my_list) <- c(“v”, “m”, “df”)
if(group_type == "BNB"){
  v_name <- substr(b, 9, 11)
} else if(group_type == "B"){
  v_name <- substr(b, 7, 9)
} else {
  v_name <- substr(b, 8, 10)
}

names(gmm.list) <- v_name

##output gbi objects[gbi_gmm.list]----
gbi_gmm.list <- list()
for(i in 1:length(gmm.list)) {
    outputname <- paste0("gbi_", names(gmm.list)[i])
    assign(outputname, gmm.list[[i]][[1]]) #fill in adjacency matrix
    gbi_gmm.list[[i]] <- gmm.list[[i]][[1]]
    names(gbi_gmm.list)[i] <- outputname  # name each object
}

#get adjacency matrix[adjm_gmm.list]----
adjm_gmm.list <- lapply(gbi_gmm.list, asnipe::get_network, data_format = "GBI", association_index = index)

#id list for birds with no association
idzero.list <- lapply(gbi_gmm.list, colSums) %>% map(~ names(.[.==0]))

#[adjm_gmm_nonz.list]----
 adjm_gmm_nonz.list <- list()

 for(i in 1: length(adjm_gmm.list)){
  adjm_gmm_nonz.list[[i]] <- adjm_gmm.list[[i]][!rownames(adjm_gmm.list[[i]]) %in% idzero.list[[i]], !colnames(adjm_gmm.list[[i]]) %in% idzero.list[[i]]]
 }

#rename your adjm list
name_adjm <- paste0("adjm_", substr(names(adjm_gmm.list), 5, 7))
names(adjm_gmm_nonz.list) <- name_adjm
names(adjm_gmm.list) <- name_adjm

                  
#get igraph object
#[net_gmm.list]----
net_gmm.list <- lapply(adjm_gmm_nonz.list, igraph::graph.adjacency, mode = "undirected", diag = F, weighted = T) #this include inds with zero association

#rename your net list
name_net <- paste0("net_", substr(names(net_gmm.list), 6, 8))
names(net_gmm.list) <- name_net
```

#save file
```{r}
#daytime
saveRDS(gbi_gmm.list, paste0("../output/data/network/plot/gmm/gbi_D_plot_gmm_SS_all_", index, "_v", cutoff, ".list.RData"))
saveRDS(net_gmm.list, paste0("../output/data/network/plot/gmm/net_D_plot_gmm_SS_all_", index, "_v", cutoff, ".list.RData"))
saveRDS(adjm_gmm.list, paste0("../output/data/network/plot/gmm/adjm_D_plot_gmm_SS_all_", index, "_v", cutoff, ".list.RData"))
```

#Find daytime groups
### Generate _dist_ and _community_ objects
```{r}
#[dist.list]dist object from association matrix----
dist.list <- lapply(adjm_gmm_nonz.list, function(x)as.dist(1-x, diag = FALSE, upper = FALSE))

```

### CCC score 
##### Compare hierarchical clustering methods (this can skip)
```{r}
#function to calculate ccc scores
f_ccc <- function(d){ #d is the dist object
#Hierarchical clustering
  hc.c <- hclust(d, method = "complete") 
  hc.w <- hclust(d, method = "ward.D") 
  hc.w2 <- hclust(d, method = "ward.D2")
  hc.s <- hclust(d, method = "single") 
  hc.a <- hclust(d, method = "average") 
  
  #evaluate assocation between clustering results and original association matrix
  #calculate Cophetic distance(>0.75 means the method is good)
  coph.c <- cor(cophenetic(hc.c), as.dist(d))
  coph.w <- cor(cophenetic(hc.w), as.dist(d))
  coph.w2 <- cor(cophenetic(hc.w2), as.dist(d))
  coph.s <- cor(cophenetic(hc.s), as.dist(d))
  coph.a <- cor(cophenetic(hc.a), as.dist(d))
  #coph.fg <- cor(cophenetic(hc.fg), as.dist(d))

  v <- rbind(coph.c, coph.w, coph.w2, coph.s, coph.a) %>% as.data.frame() %>% setDT(., keep.rownames = "method") %>% rename(CCC=V1) %>% arrange(desc(CCC))
  
  return(v)
}
```

```{r}
#[ccc_best.df]choose the best clustering method----
ccc.list <- lapply(dist.list, f_ccc) 
ccc.df <- do.call(rbind, ccc.list) %>% rownames_to_column("colony") %>% mutate(colony = substr(colony, 6, 16)) 
ccc_best.df <- ccc.df %>% group_by(colony) %>% arrange(-CCC) %>%  slice(1) %>% ungroup() 
print(ccc_best.df)
```
## Conclusion: AVERAGE-linkage has the highest score (agree with Whitehead's observation)


#find the cutoff point for dendrogram
#method: optimization of modularity
```{r}
#[hca.list]hclust object for average-linkage methods----
hca.list <- lapply(dist.list, function(x)hclust(x, method = "average")) 


#function to calculate $modularity and $n_group for each branch height
cutoff.list <- list()

for(i in 1:length(hca.list)){
  hca <- hca.list[[i]]
  netname <- paste0("net_", substr(names(hca.list)[i], 6, 8))
  net <- net_gmm.list[[netname]]
  height <- hca$height  #branch height
  
  n_group <- vector() #number of groups
  mod <- vector() #modularity
  association <- vector()
  
  for(j in 1:length(height)){
    grp <- cutree(hca, h = height[j]) #group membership
  
    a <- max(grp) #number of groups
    b <- modularity(net, membership = grp, weights = E(net)$weight) #modularity
  
    n_group[j] <- a
    mod[j] <- b
    association[j] <- 1-height[j]
    
  }  #end of j loop
  
  cutoff.list[[i]] <- data.frame(n_group, mod, association) %>% mutate(net = netname) %>% mutate(diff_mod = round(lead(mod)-mod, 4), diff_asso = round(lead(association)-association, 4))
} #end of i loop

#[cutoff.df]----
cutoff.df <- rbindlist(cutoff.list) %>% 
  mutate(year = paste0("20", substr(net, 5, 6)), 
         plot = substr(net, 7, 7)) %>% 
  mutate(plot = dplyr::recode(plot, "M" = "MSTO", "S" = "SPRA", "L" = "LLOD")) %>% 
  mutate(mod = round(mod, digits = 3), association = round(association, digits = 3))

#[cutoff.df.l]----
#gather modularity and association
cutoff.df.l <- cutoff.df %>% 
  gather(., key = "measure", value = "value", c("mod", "association")) %>% 
  gather(., key = "delta_measure", value = "delta", c("diff_mod", "diff_asso"))

#[max_mod]maximum modularity----
#this has not filtered out the assocation below random
#this has not filtered only "colony members"
#because these data include random visitors, some of modularities are very low
max_mod <- cutoff.df %>% 
  select(-diff_mod, -diff_asso) %>% 
  distinct() %>% 
  group_by(net) %>% 
  slice(which(mod == max(mod))) %>% #select the cutoff with highest modularity
  mutate(mod = round(mod, 5)) %>% 
  group_by(net) %>% 
  mutate(n = sum(n())) %>% 
  filter(n_group == max(n_group)) %>% #choose the max number of groups in the case where there are more than two cutoff with the highest modularity
  setDT()

#write_xlsx(max_mod, paste0("../output/cluster analysis/data/max_modularity_hc_gmm_all_D_", group_type, "_v", cutoff, "_", group_type, ".xlsx"))
```


## output group membership from hierarchical clustering
```{r}
#function to generate group membership
group_hca.list <- list()

for(i in 1:length(hca.list)){
  hca <- hca.list[[i]]
  netname <- paste0("net_", substr(names(hca.list)[i], 6, 8))
  v_year <- paste0("20", substr(netname, 5,6))
  v_plot <- substr(netname, 7, 7)

  grp <- cutree(hca, k = max_mod[net==netname]$n_group) #or k= (number of groups) as opposed to h
  group_hc <- reshape2::melt(grp, value.name = "group") %>% 
    rownames_to_column("color") %>% 
    arrange(group) %>% 
    mutate(net = netname, 
           year = v_year, 
           plot = v_plot, 
           groupid = paste0(substr(v_year, 3, 4), substr(v_plot, 1, 1), g_type2, "g", group))
  
  group_hca.list[[i]] <- group_hc  #group member list
} 

#[group_member_hc]output group members from hierarchical clustering----
group_member_hc <- rbindlist(group_hca.list) %>% mutate(gtype = g_type) %>% mutate(plot = recode(plot, "M" = "MSTO", "S" = "SPRA","L" = "LLOD"))
```

```{r}
saveRDS(group_member_hc, paste0("../output/cluster analysis/data/plot/2013-2017 weaver groups_D_plot_SS_all_", data_type, "_", index, "_v", cutoff,"_hc", ".RData"))

write_xlsx(group_member_hc, paste0("../output/cluster analysis/data/plot/2013-2017 weaver groups_D_plot_SS_all_", data_type, "_", index, "_v", cutoff,"_hc", ".xlsx"))
```

#-----------NIGHTTIME-------------#
```{r}
cutoff = 0
group_type = "NB"  #"BNB", "B", "NB"
#status = 0  #0=BNB, 1=B
index = "SRI"
format = "gbi"

g_type = "N" #nighttime
subgroup = "nb" #"nb", "b", ""(BNB)
```

#for sleepnest, only systematic sampling
```{r}
source("fun_N_net.R")

#[sleepnest_ss]----
sleepnest_ss <- sleepnest %>%  
  left_join(select(colonywise_sampledate, colony, date, colony_sampled), 
            by = c("colony", "sleep_date" = "date")) %>% 
  left_join(select(colony_excluded, year, colony, excluded), by = c("year", "colony")) %>%
    mutate(excluded = replace_na(excluded, 0)) %>% #add $excluded, colonies only active in Mar or Jun
  filter(colony_sampled == 1) #$colony_sampled is for nighttime

output.ls <- sleepnest_ss %>% 
  left_join(sum_bird_nest_BNB, by = c("year", "plot", "colony", "color", "nest")) %>%
  mutate(BNB_visit = replace_na(BNB_visit, 0), 
         B_visit = replace_na(B_visit, 0)) %>% 
  #mutate(breeding = if_else(!is.na(nestid), 1, 0)) %>% 
  #filter(breeding >= status) %>% #breeding or non-breeding
  filter(no_nights > cutoff) %>% #cutoff 
  setDT() %>% 
  split(list(.$year, .$plot), drop = T) %>% 
  map(~ fun_N_net(., group_type, index, format)) 

# output adjacency objects [adj.list]----
adjm.list <- list()
for(i in 1:length(output.ls)) {
    outputname <- paste0("adjm_", substr(names(output.ls)[i], 3, 4), substr(names(output.ls)[i], 6, 6)) #eg. adjm_15L
    adjm.list[[i]] <- output.ls[[i]][[1]]
    names(adjm.list)[i] <- outputname  # name each object
}


# output igraph objects [net.list]----
net.list <- list()
for(i in 1:length(output.ls)) {
    outputname <- paste0("net_", substr(names(output.ls)[i], 3, 4), substr(names(output.ls)[i], 6, 6)) #eg. adjm_15L
    net.list[[i]] <- output.ls[[i]][[2]]
    names(net.list)[i] <- outputname  # name each object
}

# saveRDS(net.list, paste0("../output/data/network/plot/net_N_plot_", group_type, "_SS_all_" ,index, "_v", cutoff, ".list.RData"))
# saveRDS(adjm.list, paste0("../output/data/network/plot/adjm_N_plot_", group_type, "_SS_all_" ,index, "_v", cutoff, ".list.RData"))
```


#-----Nightime Breeding--------#
```{r}
cutoff = 0
group_type = "B"  #"BNB", "B", "NB"
#status = 0  #0=BNB, 1=B
index = "SRI"
format = "gbi"

g_type = "N" #nighttime
subgroup = "b" #"nb", "b", ""(BNB)
```

#for sleepnest, all sampling
```{r}
source("fun_N_net.R")

# #[sleepnest_ss]----
# sleepnest_ss <- sleepnest %>%  
#   left_join(select(colonywise_sampledate, colony, date, colony_sampled), 
#             by = c("colony", "sleep_date" = "date")) %>% 
#   left_join(select(colony_excluded, year, colony, excluded), by = c("year", "colony")) %>%
#     mutate(excluded = replace_na(excluded, 0)) %>% #add $excluded, colonies only active in Mar or Jun
#   filter(colony_sampled == 1) #$colony_sampled is for nighttime

output.ls <- sleepnest %>% 
  left_join(sum_bird_nest_BNB, by = c("year", "plot", "colony", "color", "nest")) %>%
  mutate(BNB_visit = replace_na(BNB_visit, 0), 
         B_visit = replace_na(B_visit, 0)) %>% 
  #mutate(breeding = if_else(!is.na(nestid), 1, 0)) %>% 
  #filter(breeding >= status) %>% #breeding or non-breeding
  filter(no_nights > cutoff) %>% #cutoff 
  setDT() %>% 
  split(list(.$year, .$plot), drop = T) %>% 
  map(~ fun_N_net(., group_type, index, format)) 

# output adjacency objects [adj.list]----
adjm.list <- list()
for(i in 1:length(output.ls)) {
    outputname <- paste0("adjm_", substr(names(output.ls)[i], 3, 4), substr(names(output.ls)[i], 6, 6)) #eg. adjm_15L
    adjm.list[[i]] <- output.ls[[i]][[1]]
    names(adjm.list)[i] <- outputname  # name each object
}


# output igraph objects [net.list]----
net.list <- list()
for(i in 1:length(output.ls)) {
    outputname <- paste0("net_", substr(names(output.ls)[i], 3, 4), substr(names(output.ls)[i], 6, 6)) #eg. adjm_15L
    net.list[[i]] <- output.ls[[i]][[2]]
    names(net.list)[i] <- outputname  # name each object
}

# saveRDS(net.list, paste0("../output/data/network/plot/net_N_plot_", group_type, "_", index, "_v", cutoff, ".list.RData"))
# saveRDS(adjm.list, paste0("../output/data/network/plot/adjm_N_plot_", group_type, "_", index, "_v", cutoff, ".list.RData"))
```

#----------------------------------------------------
#Now use cluster analysis to get nightitme groups

### Generate _dist_ and _community_ objects
```{r}
#[dist.list]dist object from association matrix----
dist_N.list <- lapply(adjm.list, function(x)as.dist(1-x, diag = FALSE, upper = FALSE))
```

### CCC score 
##### Compare hierarchical clustering methods
```{r}
#function to calculate ccc scores:f_ccc (Line68, same as daytime)
f_ccc <- function(d){ #d is the dist object
#Hierarchical clustering
  hc.c <- hclust(d, method = "complete") 
  hc.w <- hclust(d, method = "ward.D") 
  hc.w2 <- hclust(d, method = "ward.D2")
  hc.s <- hclust(d, method = "single") 
  hc.a <- hclust(d, method = "average") 
  
  #evaluate assocation between clustering results and original association matrix
  #calculate Cophetic distance(>0.75 means the method is good)
  coph.c <- cor(cophenetic(hc.c), as.dist(d))
  coph.w <- cor(cophenetic(hc.w), as.dist(d))
  coph.w2 <- cor(cophenetic(hc.w2), as.dist(d))
  coph.s <- cor(cophenetic(hc.s), as.dist(d))
  coph.a <- cor(cophenetic(hc.a), as.dist(d))
  #coph.fg <- cor(cophenetic(hc.fg), as.dist(d))

  v <- rbind(coph.c, coph.w, coph.w2, coph.s, coph.a) %>% as.data.frame() %>% setDT(., keep.rownames = "method") %>% rename(CCC=V1) %>% arrange(desc(CCC))
  
  return(v)
}

#[ccc_best.df]choose the best clustering method----
ccc_N.list <- lapply(dist_N.list, f_ccc) 
ccc_N.df <- do.call(rbind, ccc_N.list) %>% rownames_to_column("plot") %>% mutate(plot = substr(plot, 6, 14)) 
ccc_N_best.df <- ccc_N.df %>% group_by(plot) %>% arrange(-CCC) %>% dplyr:: slice(1) %>% ungroup() 
print(ccc_N_best.df)
```
## Conclusion: AVERAGE-linkage has the highest score (agree with Whitehead's observation)


#find the cutoff point for dendrogram
#method: optimization of modularity
```{r}
#[hca.list]hclust object for average-linkage methods----
hca_N.list <- lapply(dist_N.list, function(x)hclust(x, method = "average")) 


#function to calculate $modularity and $n_group for each branch height
cutoff_N.list <- list()
for(i in 1:length(hca_N.list)){
  hca <- hca_N.list[[i]]
  netname <- paste0("net_", substr(names(hca_N.list)[i], 6, 16))
  net <- net.list[[netname]]
  height <- hca$height  #branch height
  
  n_group <- vector() #number of groups
  mod <- vector() #modularity
  association <- vector()
  
  for(j in 1:length(height)){
    grp <- cutree(hca, h = height[j]) #group membership
  
    a <- max(grp) #number of groups
    b <- modularity(net, membership = grp, weights = E(net)$weight) #modularity
  
    n_group[j] <- a
    mod[j] <- b
    association[j] <- 1-height[j]
    
  }  #end of j loop
  
  cutoff_N.list[[i]] <- data.frame(n_group, mod, association) %>% mutate(net = netname) %>% mutate(diff_mod = round(lead(mod)-mod, 4), diff_asso = round(lead(association)-association, 4))
} #end of i loop

#[cutoff_N.df]----
cutoff_N.df <- rbindlist(cutoff_N.list)

#[max_mod_N]maximum modularity----
max_mod_N <- cutoff_N.df %>% 
  select(-diff_mod, -diff_asso) %>% 
  distinct() %>% 
  group_by(net) %>% 
  dplyr::slice(which(mod == max(mod))) %>% #select the cutoff with highest modularity
  mutate(mod = round(mod, 2)) %>% 
  group_by(net) %>% 
  mutate(n = sum(n())) %>% 
  filter(association == max(association)) %>% #if there are two cutoff with same modularity, select the cutoff at highter association (bc the lower association are all ZERO)
  setDT()

#write_xlsx(max_mod_N, paste0("../output/cluster analysis/data/max_modularity_hc_N_SS_all_", group_type, "_v", cutoff, "_", ".xlsx"))
```

## output group membership from hierarchical clustering
```{r}
#function to generate group membership
group_hca_N.list <- list()
for(i in 1:length(hca_N.list)){
  hca <- hca_N.list[[i]]
  netname <- paste0("net_", substr(names(hca_N.list)[i], 6, 14))
  v_year <- paste0("20", substr(netname, 5,6))
  v_plot <- substr(netname, 7, 7)

  grp <- cutree(hca, k = max_mod_N[net==netname]$n_group)#or k= (number of groups) as opposed to h
  group_hc <- reshape2::melt(grp, value.name = "group") %>% 
    rownames_to_column("color") %>% 
    arrange(group) %>% 
    mutate(net = netname, 
           year = v_year, 
           plot = recode(v_plot, "M" = "MSTO", "S" = "SPRA", "L" = "LLOD"),
           groupid = paste0(substr(v_year, 3, 4), substr(v_plot, 1, 1), g_type, "g", group, subgroup))
  
  group_hca_N.list[[i]] <- group_hc  #group member list
} 

#[group_member_hc]output group members from hierarchical clustering----
group_member_N_hc <- rbindlist(group_hca_N.list) %>% mutate(gtype = "sleeping") #if"BNB"
group_member_N_hc <- rbindlist(group_hca_N.list) %>% mutate(gtype = "sleepingNB") #if NB
group_member_N_hc <- rbindlist(group_hca_N.list) %>% mutate(gtype = "sleepingB") #if B
```

#save data
```{r}
#Systematic sampling
saveRDS(group_member_N_hc, paste0("../output/cluster analysis/data/plot/2013-2017 weaver groups_N_plot_SS_all_", group_type, "_", index, "_v", cutoff,"_hc", ".RData"))

write_xlsx(group_member_N_hc, paste0("../output/cluster analysis/data/plot/2013-2017 weaver groups_N_plot_SS_all_", group_type, "_", index, "_v", cutoff,"_hc", ".xlsx"))
```

```{r}
#ALL sampling
saveRDS(group_member_N_hc, paste0("../output/cluster analysis/data/plot/2013-2017 weaver groups_N_plot_", group_type, "_", index, "_v", cutoff,"_hc", ".RData"))

write_xlsx(group_member_N_hc, paste0("../output/cluster analysis/data/plot/2013-2017 weaver groups_N_plot_", group_type, "_", index, "_v", cutoff,"_hc", ".xlsx"))
```
#--------END of nighttime-------------#



#--------NESTLING----------#
#Generate adjacency matrix and network objects

```{r}
cutoff = 3
group_type = "NSTL"  #"BNB", "B", "NB"
index = "SRI"
format = "gbi"

g_type = "nestling" #nighttime
g_type2 = "B"
subgroup = "nstl"
```

```{r}
#this can run for a long time for a big data set
fun_gmm2 <- function(daytime){
  point_data_all <- daytime %>% 
    filter(sec > 0) %>%  #exclude data outside sampling range
    select(date, timestamp.1m, color, nest, nestdate_sec) %>%   #$nest_date as $location
    mutate(date = yday(date)) %>%  #convert to julian day
    mutate(timestamp.1m = as.numeric(timestamp.1m)) %>% setDT()
  
  sec_l2 <- point_data_all %>% count(nestdate_sec) %>% filter(n > 2)
  
  point_data <- point_data_all %>% filter(nestdate_sec %in% sec_l2$nestdate_sec)
  
  global_ids <- levels(point_data$color)
  
  gmm_data <- asnipe::gmmevents(time = point_data$timestamp.1m,
                                identity = point_data$color,
                                location = point_data$nestdate_sec,
                                global_ids=global_ids
  )
  #group name to add in the filename
  groupname <- paste0(substr(unique(daytime$year), 3, 4), substr(unique(daytime$plot), 1, 1))
  
  #output your gmm data!!
  saveRDS(gmm_data, file = paste0("../output/data/gmm/NSTL/v",cutoff,"/gmm_NSTL_", groupname, "_v",cutoff, ".RData"))
  
}
#------end of function----#
```




```{r}
sum_Bvisit_nstl <- dayvisit_B %>% 
  filter(stageB == "NSTL") %>% 
  group_by(nestid, color) %>% 
  summarise(sum_visit = sum(no_visits)) %>% 
  group_by(nestid) %>% 
  mutate(pro = round(sum_visit/sum(sum_visit), digits = 2))

hist_Bvisit_nstl <- sum_Bvisit_nstl %>% 
  group_by(sum_visit) %>% 
  count(sum_visit) %>% setDT()

#to cutoff
id_excluded <- sum_Bvisit_nstl %>% 
  filter(sum_visit <= cutoff) %>% 
  select(nestid, color) %>% 
  mutate(excluded=1)
```


#Generate gbi data (this runs a long time)
```{r}
#output gmm data by year, plot
nstl.list <- daytime %>%
  left_join(select(BD, nest, date, nestid, stageA), by=c("nest", "date")) %>% 
  filter(stageA=="NSTL") %>% 
  left_join(id_excluded, by=c("nestid", "color")) %>% 
  filter(is.na(excluded)) %>% 
  split(list(.$year, .$plot), drop = T)

lapply(nstl.list, fun_gmm2)
```


```{r}
#import gmm files, 
b <- list.files(paste0("../output/data/gmm/NSTL/v",cutoff,"/"))

#generate list with gbi and event
f <- function(b){
  a <- readRDS(paste0("../output/data/gmm/NSTL/v",cutoff,"/", b))
  
  event <- a$metadata %>% 
    mutate(date = str_split_fixed(Location, "_", n=3)[,2], 
         nest = str_split_fixed(Location, "_", n=3)[,1]) %>% 
    mutate(date = lubridate::mdy(date), 
           year = as.character(year(date))) %>%
    mutate(duration_min = (End - Start)/60) %>% #sampling intervals 
    left_join(nest_list_uni, by = c("nest")) %>%  #add $colony
    setDT()
  
  #only systematic sampling and <2hrs sampling interval
  position_nstl <- which(event$duration_min <=120)
  
  event_select <- event[position_nstl,]
  gbi <- a$gbi[position_nstl, ]
  nzindex <- which(colSums(gbi)>0)
  gbi <- gbi[,nzindex]
  
  outputlist <- list("gbi" = gbi, "event" = event_select)
  return(outputlist)
}

# make a list for gmm data from all plots, years
gmm.list <- lapply(b, f)  

# add name to the list
#names(my_list) <- c(“v”, “m”, “df”)

v_name <- substr(b, 10, 12)


names(gmm.list) <- v_name

##output gbi objects[gbi_gmm.list]----
gbi_gmm.list <- list()
for(i in 1:length(gmm.list)) {
    outputname <- paste0("gbi_", names(gmm.list)[i])
    assign(outputname, gmm.list[[i]][[1]]) #fill in adjacency matrix
    gbi_gmm.list[[i]] <- gmm.list[[i]][[1]]
    names(gbi_gmm.list)[i] <- outputname  # name each object
}

#get adjacency matrix[adjm_gmm.list]----
adjm_gmm.list <- lapply(gbi_gmm.list, asnipe::get_network, data_format = "GBI", association_index = index)

#id list for birds with no association
idzero.list <- lapply(gbi_gmm.list, colSums) %>% map(~ names(.[.==0]))

#[adjm_gmm_nonz.list]----
 adjm_gmm_nonz.list <- list()

 for(i in 1: length(adjm_gmm.list)){
  adjm_gmm_nonz.list[[i]] <- adjm_gmm.list[[i]][!rownames(adjm_gmm.list[[i]]) %in% idzero.list[[i]], !colnames(adjm_gmm.list[[i]]) %in% idzero.list[[i]]]
 }

#rename your adjm list
name_adjm <- paste0("adjm_", substr(names(adjm_gmm.list), 5, 7))
names(adjm_gmm_nonz.list) <- name_adjm
names(adjm_gmm.list) <- name_adjm

                  
#get igraph object
#[net_gmm.list]----
net_gmm.list <- lapply(adjm_gmm_nonz.list, igraph::graph.adjacency, mode = "undirected", diag = F, weighted = T) #this include inds with zero association

#rename your net list
name_net <- paste0("net_", substr(names(net_gmm.list), 6, 8))
names(net_gmm.list) <- name_net
```

#save file
```{r}
#daytime
saveRDS(gbi_gmm.list, paste0("../output/data/network/plot/gmm/gbi_D_plot_gmm_NSTL_", index, "_v",cutoff, ".list.RData"))
saveRDS(net_gmm.list, paste0("../output/data/network/plot/gmm/net_D_plot_gmm_NSTL_", index, "_v",cutoff, ".list.RData"))
saveRDS(adjm_gmm.list, paste0("../output/data/network/plot/gmm/adjm_D_plot_gmm_NSTL_", index, "_v",cutoff, ".list.RData"))
```

#Find NSTL groups
### Generate _dist_ and _community_ objects
```{r}
#[dist.list]dist object from association matrix----
dist.list <- lapply(adjm_gmm_nonz.list, function(x)as.dist(1-x, diag = FALSE, upper = FALSE))

```

### CCC score 
##### Compare hierarchical clustering methods (this can skip)
```{r}
#function to calculate ccc scores
f_ccc <- function(d){ #d is the dist object
#Hierarchical clustering
  hc.c <- hclust(d, method = "complete") 
  hc.w <- hclust(d, method = "ward.D") 
  hc.w2 <- hclust(d, method = "ward.D2")
  hc.s <- hclust(d, method = "single") 
  hc.a <- hclust(d, method = "average") 
  
  #evaluate assocation between clustering results and original association matrix
  #calculate Cophetic distance(>0.75 means the method is good)
  coph.c <- cor(cophenetic(hc.c), as.dist(d))
  coph.w <- cor(cophenetic(hc.w), as.dist(d))
  coph.w2 <- cor(cophenetic(hc.w2), as.dist(d))
  coph.s <- cor(cophenetic(hc.s), as.dist(d))
  coph.a <- cor(cophenetic(hc.a), as.dist(d))
  #coph.fg <- cor(cophenetic(hc.fg), as.dist(d))

  v <- rbind(coph.c, coph.w, coph.w2, coph.s, coph.a) %>% as.data.frame() %>% setDT(., keep.rownames = "method") %>% rename(CCC=V1) %>% arrange(desc(CCC))
  
  return(v)
}
```

```{r}
#[ccc_best.df]choose the best clustering method----
ccc.list <- lapply(dist.list, f_ccc) 
ccc.df <- do.call(rbind, ccc.list) %>% rownames_to_column("colony") %>% mutate(colony = substr(colony, 6, 16)) 
ccc_best.df <- ccc.df %>% group_by(colony) %>% arrange(-CCC) %>%  slice(1) %>% ungroup() 
print(ccc_best.df)
```
## Conclusion: AVERAGE-linkage has the highest score (agree with Whitehead's observation)


#find the cutoff point for dendrogram
#method: optimization of modularity
```{r}
#[hca.list]hclust object for average-linkage methods----
hca.list <- lapply(dist.list, function(x)hclust(x, method = "average")) 


#function to calculate $modularity and $n_group for each branch height
cutoff.list <- list()

for(i in 1:length(hca.list)){
  hca <- hca.list[[i]]
  netname <- paste0("net_", substr(names(hca.list)[i], 6, 8))
  net <- net_gmm.list[[netname]]
  height <- hca$height  #branch height
  
  n_group <- vector() #number of groups
  mod <- vector() #modularity
  association <- vector()
  
  for(j in 1:length(height)){
    grp <- cutree(hca, h = height[j]) #group membership
  
    a <- max(grp) #number of groups
    b <- modularity(net, membership = grp, weights = E(net)$weight) #modularity
  
    n_group[j] <- a
    mod[j] <- b
    association[j] <- 1-height[j]
    
  }  #end of j loop
  
  cutoff.list[[i]] <- data.frame(n_group, mod, association) %>% mutate(net = netname) %>% mutate(diff_mod = round(lead(mod)-mod, 4), diff_asso = round(lead(association)-association, 4))
} #end of i loop

#[cutoff.df]----
cutoff.df <- rbindlist(cutoff.list) %>% 
  mutate(year = paste0("20", substr(net, 5, 6)), 
         plot = substr(net, 7, 7)) %>% 
  mutate(plot = dplyr::recode(plot, "M" = "MSTO", "S" = "SPRA", "L" = "LLOD")) %>% 
  mutate(mod = round(mod, digits = 3), association = round(association, digits = 3))

#[cutoff.df.l]----
#gather modularity and association
cutoff.df.l <- cutoff.df %>% 
  gather(., key = "measure", value = "value", c("mod", "association")) %>% 
  gather(., key = "delta_measure", value = "delta", c("diff_mod", "diff_asso"))

#[max_mod]maximum modularity----
#this has not filtered out the assocation below random
#this has not filtered only "colony members"
#because these data include random visitors, some of modularities are very low
max_mod <- cutoff.df %>% 
  select(-diff_mod, -diff_asso) %>% 
  distinct() %>% 
  group_by(net) %>% 
  slice(which(mod == max(mod))) %>% #select the cutoff with highest modularity
  mutate(mod = round(mod, 5)) %>% 
  group_by(net) %>% 
  mutate(n = sum(n())) %>% 
  filter(n_group == max(n_group)) %>% #choose the max number of groups in the case where there are more than two cutoff with the highest modularity
  setDT()

#write_xlsx(max_mod, paste0("../output/cluster analysis/data/max_modularity_hc_gmm_all_D_", group_type, "_v", cutoff, "_", group_type, ".xlsx"))
```


## output group membership from hierarchical clustering
```{r}
#function to generate group membership
group_hca.list <- list()

for(i in 1:length(hca.list)){
  hca <- hca.list[[i]]
  netname <- paste0("net_", substr(names(hca.list)[i], 6, 8))
  v_year <- paste0("20", substr(netname, 5,6))
  v_plot <- substr(netname, 7, 7)

  grp <- cutree(hca, k = max_mod[net==netname]$n_group) #or k= (number of groups) as opposed to h
  group_hc <- reshape2::melt(grp, value.name = "group") %>% 
    rownames_to_column("color") %>% 
    arrange(group) %>% 
    mutate(net = netname, 
           year = v_year, 
           plot = v_plot, 
           groupid = paste0(substr(v_year, 3, 4), substr(v_plot, 1, 1), g_type2, "g", group, subgroup))
  
  group_hca.list[[i]] <- group_hc  #group member list
} 

#[group_member_hc]output group members from hierarchical clustering----
group_member_hc <- rbindlist(group_hca.list) %>% mutate(gtype = g_type) %>% mutate(plot = recode(plot, "M" = "MSTO", "S" = "SPRA","L" = "LLOD"))
```

```{r}
saveRDS(group_member_hc, paste0("../output/cluster analysis/data/plot/2013-2017 weaver groups_D_plot_NSTL_v",cutoff,"_hc", ".RData"))

write_xlsx(group_member_hc, paste0("../output/cluster analysis/data/plot/2013-2017 weaver groups_D_plot_NSTL_v",cutoff,"_hc", ".xlsx"))
```

#output membership object (working, but undone for all)
```{r}
f_hcmem <- function(data){
  d <- split(data["color"], data$group)
  output <- lapply(d, dplyr::pull)
  return(output)
}

mem.list <- group_member_hc %>% 
  select(net, group, color) %>% 
  split(list(.$net), drop = T) %>% 
  map(., f_hcmem)

```

